---
title: "norepeat_climate_test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
```



#{.tabset}

##Setup/Assumptions

Experiment: Simulate an initial stock assessment in Year 1 using catch-based data with varied amounts of error around the estimate of f/fmsy. Make a decision on the harvest control rule based on estimate of f/fmsy. Apply that rule to the fishing mortality in year 1 and never repeat for the remainder of the simulation.This model includes a decrease in productivity over time due to climate change (r_s term).

in this test, I am using one r_s value (-0.005), which is equivalent to a 0.5% decrease in productivity each year

Assumptions: 
 - Fisheries represented in the model have no current management. Initial biomass in the simulation is therefore representative of the equilibrium that the fishery has reached over the years due to some level of fishing mortality (f). 
 - Fishing mortality and f/fmsy ratios are calculated at the beginning of each year and the change in f is applied to fishing in that same year
 - The current f at the beginning of the simulation is reached when catch is equivalent to the surplus production of the fishery at that biomass. 
 - The f calculated at the beginning of the simulation is the true fishing mortality rate of the operating fishery. 
 - Climate change is affecting the productivity of fish stocks by influeing the growth term (r)
 
Goal: Simulate the initial use of FISHE, if it is only applied once and never repeated, focusing on the Inital Stock Assessment step of the process, with climate reducing productivity.
 
 
##Model

```{r model}

#Baseline model with error around initial stock assessment and no repetition of the stock assessment process for the duration of the simulation:

sim_norep_clim <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), f = rep(NA, years),
    f_msy = rep(NA, years), f_ratio = rep(NA, years), f_ratio_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
  results$b[1] = b
  results$r[1] = r
  f_int = (results$r[1] / p) * (1 - ((results$b[1] / k) ^ p)) #initial f assuming catch = surplus
  
  
  fmsy <-function(r,p){r * (1 / (1+p))} #set up the function to calculate Fmsy based on growth (r) and shape parameter (p)
  r_calc1 <- results$r[1]
  results$f_msy[1] <- fmsy(r=r_calc1, p=p) #calculate fmsy in year 1 based on historical parameters
  results$f_ratio[1] = f_int/results$f_msy[1] #calculate the actual f_ratio from initial fishing pressure (this is basically f in time t-1) and fmsy
  results$f_ratio_err[1] = rnorm(1, mean = results$f_ratio[1], sd = (error*results$f_ratio[1])) #simulate error in the f ratio estimate
  
  #Decide how to change f based on the f ratio estimate with error:
  if(results$f_ratio_err[1] >= 2){
       results$f[1] = 0 #Close the fishery
   } 
    if(results$f_ratio_err[1] > 1 & results$f_ratio_err[1] < 2){
       results$f[1] = 0.9*f_int #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[1] == 1){
       results$f[1] = f_int  #f stays the same in as last year
   }
    if(results$f_ratio_err[1] < 1){
       results$f[1] = 1.05*f_int #f increases by 5% from last year
   } 
  
  #Calculate catch in year one based on the new f:
  results$c[1] = results$f[1] * results$b[1] 
  
  
  ## Loop the model over the specified number of years
  # DO NOT REPEAT the initial stock assessment - f remains constant for the rest of the time
  for (t in 2:years) {
    
    #Results for the parameters that still update every year: 
    results$r[t] = results$r[1] * (1 + (r_s*(t-1))) 
    results$f[t] = results$f[1]
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$c[t] = results$f[t] * results$b[t]
    
    #Results for parameters that don't change unless it's an assessment year - for ease set these all to zero
    results$f_msy[t] = 0
    results$f_ratio[t] = 0
    results$f_ratio_err[t] = 0
    
}
  return(results)
}


```
 
##Model Check

Quick check over a simple input to be sure the model runs properly:
```{r model-check}

check_result_clim <- sim_norep_clim(b=6000, r=0.2, r_s=-0.005, error=0.10, p=0.2, k=10000, years=100)

```


##Model Inputs List

Create the experiment input list:
```{r experiment-inputs}

#Design experiments - what is the range of r_s we want to include? Do we want to test multiple velocities??
list_norep_clim <- list(
  b = seq(1000, 10000, 1000),
  r = 0.2,
  r_s = -0.005, #this is a -0.5% change in productivity per year - so 10% in 20 years
  error = seq(0.05, 0.55, 0.05),
  p = 0.2,
  k = 10000,
  years = 100
)

input_norep_clim <- list_norep_clim %>% 
  cross()


```

##Run

```{r run}
results = list()

#Run the model over the input lists:
for(i in 1:110){
  results[[i]] <- sim_norep_clim(b=input_norep_clim[[i]]$b, r=input_norep_clim[[i]]$r,
                              r_s=input_norep_clim[[i]]$r_s, p=input_norep_clim[[i]]$p, 
                              k=input_norep_clim[[i]]$k,years=input_norep_clim[[i]]$years,
                              error = input_norep_clim[[i]]$error)
}

```

##Save to CSV 

```{r save-to-csv}

input_norep_clim_test_df <- as.data.frame(matrix(unlist(input_norep_clim_test), nrow = length(unlist(input_norep_clim_test[110]))))
        
results_norep_clim_test_df <- as.data.frame(matrix(unlist(results), nrow = length(unlist(results[110]))))

norep_clim_test_df <- rbind(input_norep_clim_test_df, results_norep_clim_test_df)

norep_clim_test_df_final <- data.frame(t(norep_clim_test_df))

write.csv(norep_clim_test_df_final, "G:/Data Analysis/SomefinFishE/FISHE_tests/stock_assessment_new/catch_tests/csv_results/norep_clim_test.csv", row.names = FALSE)

#plot the results

for(i in 1:110){
 plot(results[[i]]$b)
}

```


