---
title: "rep15_noclimate"
output: html_document
---

```{r packages, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(tidyr)
```

#{.tabset}

##Setup/Assumptions

Experiment: Simulate an initial stock assessment in Year 1 using catch-based data with varied amounts of error around the estimate of f/fmsy. Make a decision on the harvest control rule based on estimate of f/fmsy. Apply that rule to the fishing mortality in that year. Repeat this process every 15 years, applying the change in f to that year.

Assumptions: 
 - Fisheries represented in the model have no current management. Initial biomass in the simulation is therefore representative of the equilibrium that the fishery has reached over the years due to some level of fishing mortality (f). 
 - Fishing mortality and f/fmsy ratios are calculated at the beginning of each year and the change in f is applied to fishing in that same year
 - The current f at the beginning of the simulation is reached when catch is equivalent to the surplus production of the fishery at that biomass. 
 - The f calculated at the beginning of the simulation is the true fishing mortality rate of the operating fishery. 
 - There are no influences of climate change on this fishery 
 
Goal: Simulate the initial use of FISHE, if it is only applied on 15 year intervals, focusing on the Inital Stock Assessment step of the process. 
 
 
##Model

Before running the model run the following code:
```{r setup}

#create an interval vector for times that we do want to do the assessment:
assess_int <- c(15,30,45,60,75,90)

#Write a "not contained in" function"
`%not_in%` <- purrr::negate(`%in%`)
```

A note about the HCR and f: the HCR decision must be applied to f in the first year otherwise f and biomass will remain constant until year 20 when the next assessment is applied. 
```{r model}

#Baseline model with error around the f_ratio (f/fmsy) and no repetition of the stock assessment process for the duration of the simulation:

sim_15 <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), f = rep(NA, years),
    f_msy = rep(NA, years), f_ratio = rep(NA, years), f_ratio_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
  results$b[1] = b
  results$r[1] = r
  f_int = (results$r[1] / p) * (1 - ((results$b[1] / k) ^ p)) #initial f assuming catch = surplus
  
  
  fmsy <-function(r,p){r * (1 / (1+p))} #set up the function to calculate Fmsy based on growth (r) and shape parameter (p)
  r_calc1 <- results$r[1]
  results$f_msy[1] <- fmsy(r=r_calc1, p=p) #calculate fmsy in year 1 based on historical parameters
  results$f_ratio[1] = f_int/results$f_msy[1] #calculate the actual f_ratio from initial fishing pressure (this is basically f in time t-1) and fmsy
  results$f_ratio_err[1] = rnorm(1, mean = results$f_ratio[1], sd = (error*results$f_ratio[1])) #simulate error in the f ratio estimate
  
  #Decide how to change f based on the f ratio estimate with error:
  if(results$f_ratio_err[1] >= 2){
       results$f[1] = 0 #Close the fishery
   } 
    if(results$f_ratio_err[1] > 1 & results$f_ratio_err[1] < 2){
       results$f[1] = 0.9*f_int #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[1] == 1){
       results$f[1] = f_int  #f stays the same in as last year
   }
    if(results$f_ratio_err[1] < 1){
       results$f[1] = 1.05*f_int #f increases by 5% from last year
   } 
  
  #Calculate catch in year one based on the new f:
  results$c[1] = results$f[1] * results$b[1] 
  
  ## Loop the model over the specified number of years
  # Repeat on 20 year intervals - make the HCR decision and apply the f to the following year, this f remains constant until next assessment
  for (t in 2:years) {
    if(results$year[t] %in% assess_int){
    
    results$r[t] = results$r[1] * (1 + (r_s*(t-1))) 
    
    ##HCR decision will change how f is calculated - this step must come before calculating c 
    # Calculate fmsy in time t from current r 
    r_calc2 <- results$r[t-1]
    results$f_msy[t] <- fmsy(r=r_calc2, p=p)
    results$f_ratio[t] <- results$f[t-1]/results$f_msy[t-1] #the ratio of f/fmsy at the beginning of the year is based on last years f and fmsy
    results$f_ratio_err[t] = rnorm(1, mean = results$f_ratio[t], sd = (error*results$f_ratio[t]))
    
    #Decisions for f this year based on the ratio with error in the previous year 
    if(results$f_ratio_err[t] >= 2){
       results$f[t] = 0 #I think it makes sense for f to be zero the rest of the years but I don't know how to write that
   } 
    if(results$f_ratio_err[t] > 1 & results$f_ratio_err[t] < 2){
       results$f[t] = 0.9*results$f[t-1] #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[t] == 1){
       results$f[t] = results$f[t-1]  #f stays the same in as last year
   }
    if(results$f_ratio_err[t] < 1){
       results$f[t] = 1.05*results$f[t-1] #f increases by 5% from last year
   } 
    
    
    #Calculate remaining results - pay attention to the order!
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$c[t] = results$f[t] * results$b[t]
   } 

  if(results$year[t] %not_in% assess_int){
    results$r[t] = results$r[1] * (1 + (r_s*(t-1)))
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$f[t] = results$f[t-1]
    results$c[t] = results$f[t] * results$b[t]
    results$f_msy[t] = results$f_msy[t-1]
    results$f_ratio_err[t] = results$f_ratio_err[t-1]
    results$f_ratio[t] = results$f_ratio[t-1]
    
  }
}
  return(results)
}


```

##Model Check

Simple results check:
```{r simple-check-fratio-error}

check_result_15 <- sim_15(b=6000, r=0.2, r_s=0, error=0.10, p=0.2, k=10000, years=100)
```

##Model Inputs List

Create the experiment input list:
```{r experiment-inputs}

#Design experiments
list_15 <- list(
  b = seq(1000, 10000, 1000),
  r = 0.2,
  r_s = 0,
  error = seq(0.05, 0.55, 0.05),
  p = 0.2,
  k = 10000,
  years = 100
)

input_15 <- list_15 %>%
  cross()


```


##Run

Run the model:
```{r run}

results = list()

#Run the model over the input lists:

for(i in 1:110){
  results[[i]] <- sim_15(b=input_15[[i]]$b, r=input_15[[i]]$r,
                             r_s=input_15[[i]]$r_s, p=input_15[[i]]$p,
                             k=input_15[[i]]$k,years=input_15[[i]]$years, 
                             error = input_15[[i]]$error)
}

```
