---
title: "lognormal"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

I think our model has a problem with the lognormal error. Here we will experiment with the draws to be sure that we're calculating it correctly:

##Calculate Lognormal Error 

Experiment with the formula for lognormal
```{r}
#Going to try this using the first set of values from the ratio_na dataframe
m <- 1.0242543 #define the mean using the f_ratio 
s <- 0.3*m #this experiment used a 0.3 error so the standard deviation is 0.3*mean

#Log transform the mean and stdev
mu <- log(m^2 / sqrt(s^2 + m^2)) #This seems wrong... its giving me the mean as a negative number 
sd <- sqrt(log(1 + (s^2 / m^2))) #This seems good this equals 0.2935 which is pretty close to the 0.3072 that was calculated as the sd we want

#This is what they do in the google example:
draw <- rlnorm(n = 100000000, meanlog = mu, sdlog = sd)
mean(draw) #This is 1.024 which is what we want but I'm not fully convinced this is right... 
sd(draw) #This is ~0.3 which is also what we want

plot(draw)

#Draw a random number using rlnorm:
f_ratio_err <- rlnorm(1, meanlog = mu, sdlog = sd) #These numbers make sense given the distribution but I'm confused about why the mean would be negative...

#Draw random number using exp(rnorm()) to compare:
log_err <- exp(rnorm(1, mean = mu, sd = sd))
f_ratio_err2 <- log(log_err) #This is not necessary! - this can sometimes make the number go negative 

#Compare with what we have in our model now:
model_err <- exp(rnorm(1, mean = m, sd = s)) #This is quite wrong... it's over 3 which seems impossible if the mean is ~1 and the stdev is ~ 0.3 
```

Okay so going forward we need to add the following code above the draws in the model:
m <- results$f_ratio[t]
s <- error * results$f_ratio[t].

mu <- log(m^2 / sqrt(s^2 + m^2))
sd <- sqrt(log(1 + (s^2 / m^2)))

And then the actual calculation of the f_ratio_err should be:
results$f_ratio_err[t] <- rlnorm(1, meanlog = mu, sdlog = sd)

##Calculation Check:
```{r calc-check}
#Calculate the lognormal error - this requires some transformation of the original data:
m_test <- 1.0245 #mean of normal distribution
s_test <- 0.5 * 1.0245 #stdev of normal distribution 

m_calc <- function(m, s){log(m^2 / sqrt(s^2 + m^2))} #calc log transformed mean
sd_calc <- function(m,s){sqrt(log(1 + (s^2 / m^2)))} #calc log transformed sd

mu_test <- m_calc(m=m_test, s=s_test) 
sd_test <- sd_calc(m=m_test, s=s_test) 


f_ratio_err <- rlnorm(1, meanlog = mu_test, sdlog = sd_test) #draw the ratio with error from the lognormal distribution (should never be negative!)
f_ratio_err2 <- exp(rnorm(1, mean = mu_test, sd = sd_test))
```
Okay this seems to work fine so now we need to try and put it into the model


##Simple Model Check

Use a model that reassesses every year:
```{r err-simple}


err <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), f = rep(NA, years), 
    m = rep(NA, years), s = rep(NA, years), mu = rep(NA, years), stdev = rep(NA, years),
    f_msy = rep(NA, years), f_ratio = rep(NA, years), f_ratio_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
  results$b[1] = b
  results$r[1] = r
  f_int = (results$r[1] / p) * (1 - ((results$b[1] / k) ^ p)) #initial f assuming catch = surplus
  
  
  fmsy <-function(r,p){r * (1 / (1+p))} #Calculate Fmsy 
  r_calc1 <- results$r[1]
  results$f_msy[1] <- fmsy(r=r_calc1, p=p) #calculate fmsy in year 1 based on historical parameters
  results$f_ratio[1] = f_int/results$f_msy[1] #calculate the actual f_ratio from initial fishing pressure (this is basically f in time t-1) and fmsy
  
  # # Define the mean and st dev transformation functions:
  # m_calc <- function(m,s){log(m^2 / sqrt(s^2 + m^2))}
  # stdev_calc <- function(s,m){sqrt(log(1 + (s^2 / m^2)))} 
  
  #Assign values to normal dist mean (m) and stdev (s):
  results$m[1] <- results$f_ratio[1] 
  results$s[1] <- error * results$m[1]
  
  #Transform to new mean (mu) and stdev (stdev)
  results$mu[1] <-  log((results$m[1]^2) / sqrt((results$s[1]^2) + (results$m[1]^2)))
  results$stdev[1] <- sqrt(log(1 + ((results$s[1]^2) / (results$m[1]^2)))) 
  
  #Draw the ratio:
  results$f_ratio_err[1] <- rlnorm(1, meanlog = results$mu[1], sdlog = results$stdev[1])
  
  #Decide how to change f based on the f ratio estimate with error:
  if(results$f_ratio_err[1] >= 2){
       results$f[1] = 0 #Close the fishery
   } 
    if(results$f_ratio_err[1] > 1.1 & results$f_ratio_err[1] < 2){
       results$f[1] = 0.9*f_int #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[1] > 1 & results$f_ratio_err[1] < 1.1){
       results$f[1] = f_int  #f stays the same in as last year
   }
    if(results$f_ratio_err[1] < 1){
       results$f[1] = 1.05*f_int #f increases by 5% from last year
   } 
  
  #Calculate catch in year one based on the f with error:
  results$c[1] = results$f[1] * results$b[1] 
  
  ## Loop the model over the specified number of years
  for (t in 2:years) {
    
    results$r[t] = results$r[t-1] + (r_s*results$r[t-1]) 
    
    ##HCR decision will change how f is calculated - this step must come before calculating c 
    # Calculate fmsy in time t from current r 
    r_calc2 <- results$r[t]
    results$f_msy[t] <- fmsy(r=r_calc2, p=p)
    results$f_ratio[t] <- results$f[t-1]/results$f_msy[t-1] #the ratio of f/fmsy at the beginning of the year is based on last years f and fmsy

    #Assign values to normal dist mean (m) and stdev (s):
    results$m[t] <- results$f_ratio[t]
    results$s[t] <- error * results$m[t]
    # mcalc2 <- results$m[t] 
    # scalc2 <- results$s[t]
  
    #Transform to new mean (mu) and stdev (stdev)
    if(results$f_ratio[t] != 0){
       results$mu[t] <-  log((results$m[t]^2) / sqrt((results$s[t]^2) + (results$m[t]^2)))
       results$stdev[t] <- sqrt(log(1 + ((results$s[t]^2) / (results$m[t]^2))))
       results$f_ratio_err[t] <- rlnorm(1, meanlog = results$mu[t], sdlog = results$stdev[t])
    }
    if(results$f_ratio[t] == 0){
       results$mu[t] = 0
       results$stdev[t] = 0
       results$f_ratio_err[t] = 0
    }
    
     
    #Decisions for f this year based on the ratio with error in the previous year 
    if(results$f_ratio_err[t] >= 2){
       results$f[t] = 0
   }
    if(results$f_ratio_err[t] > 1.1 & results$f_ratio_err[t] < 2){
       results$f[t] = 0.9*results$f[t-1] #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }
    if(results$f_ratio_err[t] > 1 & results$f_ratio_err[t] < 1.1){
       results$f[t] = results$f[t-1]  #f stays the same in as last year
   }
    if(results$f_ratio_err[t] < 1){
       results$f[t] = 1.05*results$f[t-1] #f increases by 5% from last year
   }
    
    #results$f[t]= 0.9 * results$f[t-1]
    #Calculate remaining results - pay attention to the order!
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$c[t] = results$f[t] * results$b[t]
    
}
  return(results)
}

```

##Model Check

Simple results check:
```{r simple-check}

err_test <- err(b=1500, r=0.2, r_s=-0.01767, error=0.50, p=0.2, k=10000, years=10)
```
This doesn't run on the first try but if I run it a bunch of times in a row sometimes it works... when I look at the results it looks like the stdev column is never updating. 
For example: in the first year I get mu = 0.527365982	and stdev = 0.4723807 (f_ratio = 1.894467)
In year 5 I get mu = 0.264768370 and stdev =	0.4723807 (f_ratio = 1.456943)
In year 10 I get mu = -0.018743638 and stdev = 0.4723807 (f_ratio = 1.097273)

I'm going to test what the stdev should be given the f_ratio is (error = 0.5 for both):
```{r stdev-test}
##YEAR 1
#Use the same way of calculating s as the model:
s1 <- 0.5 * 1.894467

mu1 <- m_calc(m=1.894467, s=s1) #okay mu is correct 0.5273
sd1 <- stdev_calc(m=1.894467, s=s1) #stdev is also correct 0.4723

##YEAR 5
s2 <- 0.5 * 1.456943

mu2 <- m_calc(m=1.456943, s=s2)
sd2 <- stdev_calc(s=s2, m=1.456943)

##YEAR 10
s3 <- 0.5 * 1.097273

mu3 <- m_calc(m=1.097273, s=s3) #mu is correct -0.01874
sd3 <- stdev_calc(s=s3, m=1.097273) #stdev is also correct... how is that possible? 



```
The calculations have standard deviations that come out exactly the same to 15 digits... how is that possible when the input values are different????


##Input List:

Create a short list with two types of error. Use just 10 years so its easy to look through all the results
```{r inputs}
#Design experiments
list_err <- list(
  b = 1500,
  r = 0.2,
  r_s = -0.01767, 
  error = c(0.30,0.50),
  p = 0.2,
  k = 10000,
  years = 10
)

input_err <- list_err %>%
  cross()

```

##Run

Run the model:
```{r run}

results = list()

#Run the model over the input lists:

for(i in 1:2){
  results[[i]] <- err(b=input_err[[i]]$b, r=input_err[[i]]$r,
                             r_s=input_err[[i]]$r_s, p=input_err[[i]]$p,
                             k=input_err[[i]]$k,years=input_err[[i]]$years, 
                             error = input_err[[i]]$error)
}

```

Running the model over the list doesn't work. 

Does it work to run the model over each list individually?
```{r run2}

test_0.3 <- err(b=1500, r=0.2, r_s=-0.01767, error=0.30, p=0.2, k=10000, years=10)

test_0.5 <- err(b=1500, r=0.2, r_s=-0.01767, error=0.50, p=0.2, k=10000, years=10)

```
It ran over the first list but not the second one...
Again in the results for the first list the standard deviation is the same in every year... but I don't get how that's possible. 
I tried doing a few of the calculations in wolfram alpha and you do get that they're exactly the same. So either the stdev equation is wrong or that's the way its supposed to be.

Still doesn't explain why it doesn't run on the first try... and I get the results$f_ratio_err[t] >= 2 missing value where TRUE/FALSE needed error...

I'm just gonna try a lot of things and keep track of them here:

  1. Keep track of all the calc variables in the results to see where things go wrong
    - This doesn't solve the error message problem 
  
  2. Comment out the functions and just calculate the mu and stdev with the formulas directly
    - This doesn't solve the error message problem either 
    
  3. Comment out the HCR part since that's what causing the problems and set f to always decrease by 10%
    - This runs but it will produce NAN values if f_ratio is over 2 in year 1 because then the math for calculating the mean and stdev in the next years gives nonreal numbers.
  
  4. Add an if statement for the mu and stdev calcs that it only calculates them if the f_ratio is not zero
    - This seems to run fine
    
  5. Try adding the HCR part back in with the if statement for the calculations
    - Okay this seems to work now....
    
  6. Try taking the mu and stdev calculations out of the results dataframe (Cause ideally we don't actually want to track these it'll just make the results messier)
    - Okay that also worked...now I'll try adding this code into the error_updating_rep5 model....

From Chris Free's email:
```{r}
#Use an example f_ratio:
mu <- 1.894467
cv <- 0.3
mu_log <- log(mu)
sd_log <- sqrt(log(cv^2+1))
Y <- rlnorm(n=1000, meanlog = mu_log, sdlog=sd_log)
hist(Y, breaks=20, xlim=c(-0.5, 5))
```


Okay now put it into the model:
```{r}
err <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), f = rep(NA, years), 
    f_msy = rep(NA, years), f_ratio = rep(NA, years), f_ratio_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
  results$b[1] = b
  results$r[1] = r
  f_int = (results$r[1] / p) * (1 - ((results$b[1] / k) ^ p)) #initial f assuming catch = surplus
  
  
  fmsy <-function(r,p){r * (1 / (1+p))} #Calculate Fmsy 
  r_calc1 <- results$r[1]
  results$f_msy[1] <- fmsy(r=r_calc1, p=p) #calculate fmsy in year 1 based on historical parameters
  results$f_ratio[1] = f_int/results$f_msy[1] #calculate the actual f_ratio from initial fishing pressure (this is basically f in time t-1) and fmsy
  
  #Log transform the mean (m) and stdev (s):
  mu_1 <- log(results$f_ratio[1]) 
  cv <- error
  sd <- sqrt(log(cv^2+1))
  
  #Draw the f_ratio_err:
  results$f_ratio_err[1] <- rlnorm(1, meanlog = mu_1, sdlog = sd)
  
  #Decide how to change f based on the f ratio estimate with error:
  if(results$f_ratio_err[1] >= 2){
       results$f[1] = 0 #Close the fishery
   } 
    if(results$f_ratio_err[1] > 1.1 & results$f_ratio_err[1] < 2){
       results$f[1] = 0.9*f_int #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[1] > 1 & results$f_ratio_err[1] < 1.1){
       results$f[1] = f_int  #f stays the same in as last year
   }
    if(results$f_ratio_err[1] < 1){
       results$f[1] = 1.05*f_int #f increases by 5% from last year
   } 
  
  #Calculate catch in year one based on the f with error:
  results$c[1] = results$f[1] * results$b[1] 
  
  ## Loop the model over the specified number of years
  for (t in 2:years) {
    
    results$r[t] = results$r[t-1] + (r_s*results$r[t-1]) 
    
    ##HCR decision will change how f is calculated - this step must come before calculating c 
    # Calculate fmsy in time t from current r 
    r_calc2 <- results$r[t]
    results$f_msy[t] <- fmsy(r=r_calc2, p=p)
    results$f_ratio[t] <- results$f[t-1]/results$f_msy[t-1] #the ratio of f/fmsy at the beginning of the year is based on last years f and fmsy
  
    #Transform to new mean (mu) and stdev (stdev)
    if(results$f_ratio[t] != 0){
       #Assign values to normal dist mean (m) and stdev (s):
       mu_2 <- results$f_ratio[t]
       #Draw the f_ratio_err
       results$f_ratio_err[t] <- rlnorm(1, meanlog = mu_2, sdlog = sd)
    }
    if(results$f_ratio[t] == 0){
       results$f_ratio_err[t] = 0
    }
    
     
    #Decisions for f this year based on the ratio with error in the previous year 
    if(results$f_ratio_err[t] >= 2){
       results$f[t] = 0
   }
    if(results$f_ratio_err[t] > 1.1 & results$f_ratio_err[t] < 2){
       results$f[t] = 0.9*results$f[t-1] #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }
    if(results$f_ratio_err[t] > 1 & results$f_ratio_err[t] < 1.1){
       results$f[t] = results$f[t-1]  #f stays the same in as last year
   }
    if(results$f_ratio_err[t] < 1){
       results$f[t] = 1.05*results$f[t-1] #f increases by 5% from last year
   }
    
    #results$f[t]= 0.9 * results$f[t-1]
    #Calculate remaining results - pay attention to the order!
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$c[t] = results$f[t] * results$b[t]
    
}
  return(results)
}
```

