---
title: "test_shock_events"
author: "Sara Orofino"
date: "1/3/2020"
output: html_document
---
#{.tabset}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

##Purpose

We need to incorporate shock events into our model to represent El Nino years. Here is Steve's suggestion for how to do this:  

  - Error variance around the r_s term  
  - Every n years (randomly draw with probability 1/n) you have either a 10% or 30% decline in productivity  
    - Start with just 10% and 30% and see how big of a difference there is between the two  
    - Maybe start with n = 5; this is on the extreme end of what people will be experiencing   

##Randomly Assign El Nino Years

The r_s term defines how rapdily the productivity declines each year. Right now the r_s term varies from -0.01767 (1.7% decrease) to 0.01623 (1.6% increase) and this is the equation used to calculate the new growth rate in time (t) $r_t = r_{t-1} + (r_s*r_{t-1})$  

Using Steve's suggestion if we start with n = 5, then there is a 1/5 (20%) chance that you experience an El Nino event (in any given year??). My understanding is that if its an El Nino year, r will decrease by either the 10% or 30% depending on which one we are testing. In the model I think it would look something like this:   
  if(El Nino){  
  r[t] = r[t-1] + (-0.10*r[t-1]) #10% decrease of whatever your r was in the previous year    
  }  
  if(NOT El Nino){  
  r[t] = r[t-1] + (r_s*r[t-1]) #stays the same as before   
  }  

I'm a bit unclear on how we determine if it is an El Nino year or not. I'm assuming this is where the 20% part factors in but I'm not sure what that looks like exactly. My understanding is that this means there is a 20% chance that any given year is an El Nino year. So you could make a random variable (nino) and draw yes (1) or no (0) at random with a 20% chance of drawing yes (1). I found two different ways to do this:  

  - using sample()  
    -- sample(c(0,1), size=5, replace=TRUE, prob=c(0.8,0.2)) #This would also give 5 results of 1 or 0 with prob=0.8 for 0 and prob=0.2 for 1
  - using rbinom()  
    -- rbinom(5, 1,.2) #This would give me 5 results (just to test it out) of 1 or 0 where there is a prob=0.2 for getting 1

I'll test them both here to see if the results make sense   
```{r test-sample-methods}

nino1 <- sample(c(0,1), size=5, replace=TRUE, prob=c(0.8,0.2))
nino1
#First time all 0s; second time 1-1 and 4-0s; third time 2-1s and 3-0s -- seems reasonable

nino2 <- rbinom(5, 1,.2)
nino2
#First time 1-1 and 4-0s; second time all 0s; third time 1-1 and 4-0s -- also seems reasonable 
```


Let's make a quick histogram of 100 tests to double check:
```{r sample-histograms}
nino1_hist <- sample(c(0,1), size=100, replace=TRUE, prob=c(0.8,0.2))
hist(nino1_hist)
#I re-ran this several times and it always fluctuates like its supposed to around 80% 0s and 20% 1s

nino2_hist <- nino2 <- rbinom(100, 1,.2)
hist(nino2_hist)
#Also re-ran this several times and it always makes sense with what I expect
```

So I think that all together it should look vaguely something like this. This is only for one year and I'm just assigning the previous value of r for simplicity.     
```{r basic}
#For simplicity assign a value of r_t-1 and call it r_prior; assign the value of r_s; assign the value of the r decrease during el nino years
r_prior = 0.2
r_s = -0.01767
r_nino = -0.10 

#Determine if it is an El Nino year: 1 = yes and 0 = no (assume 1/5 years is an El Nino year)
nino <- rbinom(1, 1,.2) #Draw one number with a 20% chance of drawing 1 and 80% of drawing 0

if(nino==1){
  r = r_prior + (r_nino*r_prior) #if el nino year use the 10% productivity decrease
}
if(nino==0){
  r = r_prior + (r_s*r_prior) #if not el nino year use the normal r_s decrease
}

```

From what I can tell this seems to work fine. I'm not sure how this works with the assessment years though. I think drawing the el nino part would need to happen within the loop of both the assessment years and the non-assessment years because it is independent of the assessment. Then we just need to add the if statements within each loop for how to calculate r.  


##Integrate into the model

Before running the model run the following code:
```{r model-setup}

#create an interval vector for times that we do want to do the assessment:
assess_int <- seq(5,100,5)

#Write a "not contained in" function"
`%not_in%` <- purrr::negate(`%in%`)
```



Add shock events in to the model starting at year 2. Include in both assessment and non-assessment intervals. Where 0 = NO El Nino and 1 = El Nino
```{r shock-events}

sim_shock <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), nino = rep(NA, years), f = rep(NA, years),
    f_msy = rep(NA, years), f_ratio = rep(NA, years), f_ratio_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
  results$b[1] = b
  results$r[1] = r
  results$nino[1] = 0 #starting as not an el nino year
  f_int = (results$r[1] / p) * (1 - ((results$b[1] / k) ^ p)) #initial f assuming catch = surplus
  
  
  fmsy <-function(r,p){r * (1 / (1+p))} #set up the function to calculate Fmsy based on growth (r) and shape parameter (p)
  r_calc1 <- results$r[1]
  results$f_msy[1] <- fmsy(r=r_calc1, p=p) #calculate fmsy in year 1 based on historical parameters
  results$f_ratio[1] = f_int/results$f_msy[1] #calculate the actual f_ratio from initial fishing pressure (this is basically f in time t-1) and fmsy
  
  #Log transform the mean (m) and stdev (s):
  mu_1 <- log(results$f_ratio[1]) 
  cv <- error
  sd_1 <- sqrt(log(cv^2+1))
  
  #Draw the f_ratio_err:
  results$f_ratio_err[1] <- rlnorm(1, meanlog = mu_1, sdlog = sd_1)
  
  #Decide how to change f based on the f ratio estimate with error:
  if(results$f_ratio_err[1] >= 2){
       results$f[1] = 0 #Close the fishery
   } 
    if(results$f_ratio_err[1] > 1.1 & results$f_ratio_err[1] < 2){
       results$f[1] = 0.9*f_int #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[1] > 1 & results$f_ratio_err[1] < 1.1){
       results$f[1] = f_int  #f stays the same in as last year
   }
    if(results$f_ratio_err[1] < 1){
       results$f[1] = 1.05*f_int #f increases by 5% from last year
   } 
  
  #Calculate catch in year one based on the new f:
  results$c[1] = results$f[1] * results$b[1] 
  
  ## Loop the model over the specified number of years
  # Repeat on 5 year intervals - make the HCR decision and apply the f to the following year, this f remains constant until next assessment
  for (t in 2:years) {
    if(results$year[t] %in% assess_int){
    
    #Determine if it is an El Nino year:
    results$nino[t] <-  rbinom(1, 1,.2) #assuming there's a 20% chance of an El Nino in any given year
    #Define how much productivity will decrease in an El Nino year:
    r_nino <- -0.10 
    
    #Determine r[t] based on if it is an el nino year or not:
    if(results$nino[t]==1){
      results$r[t] = results$r[t-1] + (r_nino*results$r[t-1]) #in el nino year decrease by the r_nino term
    }
    if(results$nino[t]==0){
      results$r[t] = results$r[t-1] + (r_s*results$r[t-1]) #not an el nino year r calculation stays the same
    }

    
    ##HCR decision will change how f is calculated - this step must come before calculating c 
    # Calculate fmsy in time t from current r 
    r_calc2 <- results$r[t]
    results$f_msy[t] <- fmsy(r=r_calc2, p=p)
    results$f_ratio[t] <- results$f[t-1]/results$f_msy[t-1] #the ratio of f/fmsy at the beginning of the year is based on last years f and fmsy
    
    #Transform to new mean (mu) if f_ratio is greater than 0:
    if(results$f_ratio[t] != 0){
       mu_2 <- log(results$f_ratio[t])
       #Draw the f_ratio_err
       results$f_ratio_err[t] <- rlnorm(1, meanlog = mu_2, sdlog = sd_1)
    }
    if(results$f_ratio[t] == 0){
       results$f_ratio_err[t] = 0
    }

    #Decisions for f this year based on the ratio with error in the previous year 
    if(results$f_ratio_err[t] >= 2){
       results$f[t] = 0 
   } 
    if(results$f_ratio_err[t] > 1.1 & results$f_ratio_err[t] < 2){
       results$f[t] = 0.9*results$f[t-1] #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[t] > 1 & results$f_ratio_err[t] < 1.1){
       results$f[t] = results$f[t-1]  #f stays the same in as last year
   }
    if(results$f_ratio_err[t] < 1){
       results$f[t] = 1.05*results$f[t-1] #f increases by 5% from last year
   } 

    
    #Calculate remaining results - pay attention to the order!
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$c[t] = results$f[t] * results$b[t]
   } 

  if(results$year[t] %not_in% assess_int){
    
    #Determine if it is an El Nino year:
    results$nino[t] <-  rbinom(1, 1,.2) #assuming there's a 20% chance of an El Nino in any given year
    #Define how much productivity will decrease in an El Nino year:
    r_nino <- -0.10 
    
    #Determine r[t] based on if it is an el nino year or not:
    if(results$nino[t]==1){
      results$r[t] = results$r[t-1] + (r_nino*results$r[t-1]) #in el nino year decrease by the r_nino term
    }
    if(results$nino[t]==0){
      results$r[t] = results$r[t-1] + (r_s*results$r[t-1]) #not an el nino year r calculation stays the same
    }    
    
    #Calculate the remaining results:
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$f[t] = results$f[t-1]
    results$c[t] = results$f[t] * results$b[t]
    r_calc3 <- results$r[t]
    results$f_msy[t] <- fmsy(r=r_calc3, p=p)
    results$f_ratio_err[t] = results$f_ratio_err[t-1]
    results$f_ratio[t] = results$f_ratio[t-1]
    
  }
}
  return(results)
}

```

##Model Check

Simple results check:
```{r simple-check}

check_result_shock <- sim_shock(b=6000, r=0.2, r_s=-0.01767, error=0.10, p=0.2, k=10000, years=100)
```

##Model Inputs List

Create the experiment input list:
```{r experiment-inputs}

#Design experiments
list_shock <- list(
  b = c(1500, 4000, 6000),
  r = seq(0.1, .8, .1),
  r_s = seq(-0.01767, 0.01623, 0.002), 
  error = 0.3,
  p = 0.2,
  k = 10000,
  years = 100
)

input_shock <- list_shock %>%
  cross()


```


##Run

Run the model:
```{r run}

results = list()

#Run the model over the input lists:

for(i in 1:408){
  results[[i]] <- sim_shock(b=input_shock[[i]]$b, r=input_shock[[i]]$r,
                             r_s=input_shock[[i]]$r_s, p=input_shock[[i]]$p,
                             k=input_shock[[i]]$k,years=input_shock[[i]]$years, 
                             error = input_shock[[i]]$error)
}

```

So this seems to work but I haven't done enough investigating to be positive its doing everything we want. For now I'll copy it into a markdown in the tests folder and check with Steve on Thursday. 