---
title: "rep15_climate"
output: html_document
---



```{r packages, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(purrr)
library(tidyr)
```

#{.tabset}

##Setup/Assumptions

Experiment: Simulate an initial stock assessment in Year 1 using catch-based data with varied amounts of error around the estimate of f/fmsy. Make a decision on the harvest control rule based on estimate of f/fmsy. Apply that rule to the fishing mortality in that year. Repeat this process every 15 years, applying the change in f to that year.This model includes a decrease in productivity over time due to climate change (r_s term).

in this test, I am using one r_s value (-0.005), which is equivalent to a 0.5% decrease in productivity each year

Assumptions: 
 - Fisheries represented in the model have no current management. Initial biomass in the simulation is therefore representative of the equilibrium that the fishery has reached over the years due to some level of fishing mortality (f). 
 - Fishing mortality and f/fmsy ratios are calculated at the beginning of each year and the change in f is applied to fishing in that same year
 - The current f at the beginning of the simulation is reached when catch is equivalent to the surplus production of the fishery at that biomass. 
 - The f calculated at the beginning of the simulation is the true fishing mortality rate of the operating fishery. 
 - Climate change is affecting the productivity of fish stocks by influeing the growth term (r)
 - The f that comes out of the HCR is the actual f in the fishery moving forward (fisherman are adhering to that f)
 
Goal: Simulate the initial use of FISHE, if it is only applied on 15 year intervals, focusing on the Inital Stock Assessment step of the process, with climate change reducing productivity. 
 
 
##Model

Before running the model run the following code:
```{r setup}

#create an interval vector for times that we do want to do the assessment:
assess_int <- c(15,30,45,60,75,90)

#Write a "not contained in" function"
`%not_in%` <- purrr::negate(`%in%`)
```


A note about the HCR and f: the HCR decision must be applied to f in the first year otherwise f and biomass will remain constant until year 15 when the next assessment is applied. 
```{r model}

#Baseline model with error around the f_ratio (f/fmsy) and no repetition of the stock assessment process for the duration of the simulation:

sim_15c <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), f = rep(NA, years),
    f_msy = rep(NA, years), f_ratio = rep(NA, years), f_ratio_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
  results$b[1] = b
  results$r[1] = r
  f_int = (results$r[1] / p) * (1 - ((results$b[1] / k) ^ p)) #initial f assuming catch = surplus
  
  
  fmsy <-function(r,p){r * (1 / (1+p))} #set up the function to calculate Fmsy based on growth (r) and shape parameter (p)
  r_calc1 <- results$r[1]
  results$f_msy[1] <- fmsy(r=r_calc1, p=p) #calculate fmsy in year 1 based on historical parameters
  results$f_ratio[1] = f_int/results$f_msy[1] #calculate the actual f_ratio from initial fishing pressure (this is basically f in time t-1) and fmsy
  log_err = exp(rnorm(1, mean = results$f_ratio[1], sd = (error*results$f_ratio[1]))) #simulate error in the f ratio estimate
  results$f_ratio_err[1] = log(log_err)

  
  #Decide how to change f based on the f ratio estimate with error:
  if(results$f_ratio_err[1] >= 2){
       results$f[1] = 0 #Close the fishery
   } 
    if(results$f_ratio_err[1] > 1 & results$f_ratio_err[1] < 2){
       results$f[1] = 0.9*f_int #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[1] == 1){
       results$f[1] = f_int  #f stays the same in as last year
   }
    if(results$f_ratio_err[1] < 1){
       results$f[1] = 1.05*f_int #f increases by 5% from last year
   } 
  
  #Calculate catch in year one based on the new f:
  results$c[1] = results$f[1] * results$b[1] 
  
  ## Loop the model over the specified number of years
  # Repeat on 20 year intervals - make the HCR decision and apply the f to the following year, this f remains constant until next assessment
  for (t in 2:years) {
    if(results$year[t] %in% assess_int){
    
    results$r[t] = results$r[t-1] + (r_s*results$r[t-1]) 
    
    ##HCR decision will change how f is calculated - this step must come before calculating c 
    # Calculate fmsy in time t from current r 
    r_calc2 <- results$r[1]
    results$f_msy[t] <- fmsy(r=r_calc2, p=p)
    results$f_ratio[t] <- results$f[t-1]/results$f_msy[t-1] #the ratio of f/fmsy at the beginning of the year is based on last years f and fmsy
    log_err = exp(rnorm(1, mean = results$f_ratio[t], sd = (error*results$f_ratio[t]))) #simulate error in the f ratio estimate
    results$f_ratio_err[t] = log(log_err)

    
    #Decisions for f this year based on the ratio with error in the previous year 
    if(results$f_ratio_err[t] >= 2){
       results$f[t] = 0 #I think it makes sense for f to be zero the rest of the years but I don't know how to write that
   } 
    if(results$f_ratio_err[t] > 1 & results$f_ratio_err[t] < 2){
       results$f[t] = 0.9*results$f[t-1] #Reduce by 10% - same thing as keeping 90% of previous fishing mortality
   }  
    if(results$f_ratio_err[t] == 1){
       results$f[t] = results$f[t-1]  #f stays the same in as last year
   }
    if(results$f_ratio_err[t] < 1){
       results$f[t] = 1.05*results$f[t-1] #f increases by 5% from last year
   } 
    
    
    #Calculate remaining results - pay attention to the order!
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$c[t] = results$f[t] * results$b[t]
   } 

  if(results$year[t] %not_in% assess_int){
    results$r[t] = results$r[t-1] + (r_s*results$r[t-1])
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t-1]
    results$f[t] = results$f[t-1]
    results$c[t] = results$f[t] * results$b[t]
    results$f_msy[t] = results$f_msy[t-1]
    results$f_ratio_err[t] = results$f_ratio_err[t-1]
    results$f_ratio[t] = results$f_ratio[t-1]
    
  }
}
  return(results)
}


```

##Model Check

Simple results check:
```{r simple-check-fratio-error}

check_result_15c <- sim_15c(b=6000, r=0.2, r_s=-0.01767, error=0.10, p=0.2, k=10000, years=100)
```

##Model Inputs List

Create the experiment input list:
```{r experiment-inputs}

#Design experiments
list_15c <- list(
  b = c(1500, 4000, 6000),
  r = seq(0.1, .8, .05),
  r_s = seq(-0.01767, 0.01623, 0.002), 
  error = c(0.1,0.3,0.5),
  p = 0.2,
  k = 10000,
  years = 100
)

input_15c <- list_15c %>%
  cross()


```


##Run

Run the model:
```{r run}

results = list()

#Run the model over the input lists:

for(i in 1:2295){
  results[[i]] <- sim_15c(b=input_15c[[i]]$b, r=input_15c[[i]]$r,
                             r_s=input_15c[[i]]$r_s, p=input_15c[[i]]$p,
                             k=input_15c[[i]]$k,years=input_15c[[i]]$years, 
                             error = input_15c[[i]]$error)
}

```

##Save CSV
Re-run with new r equation and new r_s bounds. New results saved 12/2 (SO)
```{r save-csv}

#Create the list of column names:
col_names <- c("b", "c", "year", "r", "f", "f_msy", "f_ratio", "f_ratio_err", "id", "r_0", "error", "r_s",
               "ratio_cat", "ratio_err_cat", "correct_decision")

#Create a new list with ids
results_id <- list()

#Loop to add ids to each experiment in the list - make sure the 1:xxx matches the number of lists in the results
for(i in 1:2295){
  dat <- as.data.frame(matrix(unlist(results[i]), ncol = 8))
  dat$id <- i
  dat$r_0 <- rep(input_15c[[i]]$r, 100)
  dat$err <- rep(input_15c[[i]]$error, 100)
  dat$r_s <- rep(input_15c[[i]]$r_s, 100)
  results_id[[i]] <- dat
}


#Bind all the experiments together
results_rep15c <- bind_rows(results_id)

#Mutate columns to compare f_ratio to f_ratio_err 
results_rep15c_edit <- results_rep15c %>%
  mutate(ratio_cat = case_when(results_rep15c$V7 <= 1 ~ 0,
                               results_rep15c$V7 > 1 & results_rep15c$V7 < 2 ~ 1,
                               results_rep15c$V7 > 2 ~ 2)) %>% 
  mutate(ratio_err_cat = case_when(results_rep15c$V8 <= 1 ~ 0,
                               results_rep15c$V8 > 1 & results_rep15c$V8 < 2 ~ 1,
                               results_rep15c$V8 > 2 ~ 2)) %>%
  mutate(correct_decision = case_when(ratio_cat == ratio_err_cat ~ "TRUE",
                                      ratio_cat != ratio_err_cat ~ "FALSE"))

#Update the column names:
colnames(results_rep15c_edit) <- col_names

#Write as CSV:
# library(here)
# write.csv(results_rep15c_edit, 
#           file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep15_clim.csv"),
#           row.names = FALSE)

```
