---
title: "stockassessment_error_msy"
author: "Chase"
date: "11/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
```


##Fmsy Equation

Test the Fmsy equation:
Fmsy = r * (1 / (1+p)) - from the catchmsy function in R
```{r fmsy}

fmsy = 0.2 * (1/(1+0.2))

```

##Function
The basic function that we'll use in the rest of these tests:
```{r write_function}
#Write the function
sim_stockerror <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), b_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
   
  results$b[1] = b
  results$b_err[1] = rnorm(1, mean = results$b[1], sd = (error*results$b[1])) #simulate error in assessment
  results$c[1] = (r*(1/(1+p))) * results$b_err[1] #using f=Fmsy and b=estimate from initial stock assessment
  results$r[1] = r
  
  #Loop the model over the specified number of years
  for (t in 2:years) {
    
    results$b_err[t] = rnorm(1, mean = results$b[t-1], sd = (error*results$b[t-1]))
    results$c[t] = (r*(1/(1+p))) * results$b_err[t]
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p))-results$c[t]
    results$r[t] = results$r[1] * (1 + (r_s*(t-1))) 
    
   } 
  
  return(results)
}

results <- list()
```

##Stock Assessment
Create experiment lists
```{r create_cross_list}
# create a master list of input variables to feed into the cross() function

error_msy_experiment <- list(
  b = seq(1000, 10000, 1000),
  r = 0.2,
  r_s = 0,
  error = seq(0.05, 0.55, 0.05),
  p = 0.2,
  k = 10000,
  years = 100
)

emsye_cross <- error_msy_experiment %>% 
  cross()

# crossed lists to make 110 experiments
```

run the function
```{r run_function}

for(i in 1:110){
  results[[i]] <- sim_stockerror(b=emsye_cross[[i]]$b, r=emsye_cross[[i]]$r,
                              r_s=emsye_cross[[i]]$r_s, p=emsye_cross[[i]]$p, 
                              k=emsye_cross[[i]]$k,years=emsye_cross[[i]]$years, error = emsye_cross[[i]]$error)
}

#plot the results

for(i in 1:110){
  plot(results[[i]]$b)
}
```

##Gracie and Sara's Cross Test
To run a more complex test we'll use a longer initial list. The previous test used a list of 3 for b, r, r_s, and f. This time we'll use a list of 10 - varying b and f only.

```{r purr_test_example}

#Create the master list of input variables that will feed into the cross() function
# If the input doesn't vary in the different experiments just put one value NOT A LIST
##Note: it isn't necessary to specify n_experiments because we only need one value for constant parameters
experiment <- list(
  b = seq(1000, 10000, 1000),
  r = 0.2,
  r_s = 0,
  f = seq(0.01, 0.91, 0.1),
  p = 0.2,
  k = 10000,
  years = 50)

#Use cross() to create a master list
experiment_cross <- experiment %>%
  cross()
#Creates a list of 100 'experiments' inside each experiment are the seven parameters required to run the model
```


Loop the function where each of the lists in experiment_cross is one experiment with all the necessary input parameters to run the model
```{r purr_test_example_2}
#Set the 1:100 based on the number of lists within experiment_cross() 
for(i in 1:100){
  results[[i]] <- sim_fishery(b=experiment_cross[[i]]$b, r=experiment_cross[[i]]$r,
                              r_s=experiment_cross[[i]]$r_s, f=experiment_cross[[i]]$f, 
                              p=experiment_cross[[i]]$p, k=experiment_cross[[i]]$k,
                              years=experiment_cross[[i]]$years)
}
```
