---
title: "stockassessment_error_oa"
author: "Chase"
date: "11/13/2019"
output: html_document
---
#{.tabset}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this test is to examine a range of error magnitude over a range of initial biomasses, with fishing mortality set at open access


```{r packages}
library(tidyverse)
```


##Foa Equation

Test the Foa equation:
Foa = (r/p) * (1-
             ((0.3 ^ (p))/
                ((p+1) ^ (1+p)))
           ) - from Sara's algebra, could be right could be wrong?
           
Result Foa for r = .2 and p = .2 is .3684 - seems very plausible, we can check this by observing where fisheries that don't collapse even out. If it is around 10-15% of carrying capacity (10,000), than this should be right
```{r fmsy}

foa = (.2/.2) * (1-
             ((0.3 ^ (.2))/
                ((.2+1) ^ (1+.2)))
           )

```

##Function
The basic function that we'll use in the rest of these tests
There is no "F" variable - instead, it is the Foa equation
```{r write_function}
#Write the function
sim_stockerror_oa <- function(b, r, r_s, error, p, k, years){
  
  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), b_err = rep(NA, years)) #Setup the results dataframe 
  
  #Set the initial result for the outputs in year 1
   
  results$b[1] = b
  results$b_err[1] = rnorm(1, mean = results$b[1], sd = (error*results$b[1])) #simulate error in assessment
  results$c[1] = ((r/p) * (1- ((0.3 ^ (p)) / ((p+1) ^ (1+p))))) * results$b_err[1] #using f=Foa and b=estimate from initial stock assessment
  results$r[1] = r
  
  #Loop the model over the specified number of years
  for (t in 2:years) {
    
    results$r[t] = results$r[1] * (1 + (r_s*(t-1))) 
    results$b[t] = results$b[t-1] + (results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k) ^ p)) - results$c[t-1]
    results$b_err[t] = rnorm(1, mean = results$b[t], sd = (error*results$b[t]))
    results$c[t] = ((r/p) * (1- ((0.3 ^ (p)) / ((p+1) ^ (1+p))))) * results$b_err[t]
    
    
   } 
  
  return(results)
}

results <- list()
```

##Stock Assessment
Create experiment lists
```{r create_cross_list}
# create a master list of input variables to feed into the cross() function

error_oa_experiment <- list(
  b = seq(1000, 10000, 1000),
  r = 0.2,
  r_s = 0,
  error = seq(0.05, 0.55, 0.05),
  p = 0.2,
  k = 10000,
  years = 100
)

eoae_cross <- error_oa_experiment %>% 
  cross()

# crossed lists to make 110 experiments
```

run the function
```{r run_function}

for(i in 1:110){
  results[[i]] <- sim_stockerror_oa(b=eoae_cross[[i]]$b, r=eoae_cross[[i]]$r,
                              r_s=eoae_cross[[i]]$r_s, p=eoae_cross[[i]]$p, 
                              k=eoae_cross[[i]]$k,years=eoae_cross[[i]]$years, error = eoae_cross[[i]]$error)
}

#plot the results

#for(i in 1:110){
 # plot(results[[i]]$b)
#}
```


can we export the results as a csv?
```{r}

lapply(results, function(x) write.table(data.frame(x), 'results9.csv', sep = ' , '))
# creates a csv but only provides the last list (results[[110]])

lapply(results[[i]], function(x) write.table(data.frame(x), 'results2.csv', sep = ' , '))
# creats a csv but only provides b_err 

# trying something with json and purr that i saw online
library(jsonlite)
library(data.table)
library(purrr)

# didnt work at all so i deleted

# looping back to the lapply function that worked above but only gave the last list
# maybe if we loop it through the lists it will work

for(i in 1:110){
  lapply(results, function(x) write.table(data.frame(x), 'results6.csv', sep = ' , '))
}

#doesn't work

cross_df <- as.data.frame(matrix(unlist(eoae_cross), nrow = length(unlist(eoae_cross[110]))))
        
results_df <- as.data.frame(matrix(unlist(results), nrow = length(unlist(results[110]))))

all_df <- rbind(cross_df, results_df)

# holy shit this is working

# the as.data.frame(matrix) function is creating a data frame out of the lists that the cross() function creates. Each experiment is given it's own column, so there are 110 columns. the rows are each of the variables going into the function. 

# same for the the results df, each column is an experiment and the rows going down are biomass year after year

#It would be awesome to swap this, so each row is a an experiment with the first 7 columns being the input variables, and then 100 more columns would represent each year of biomass. Haven't tried to extract anything other than biomass yet. maybe it would be unlist(results$c) or something.

# tried using "ncol = " to switch this around but it didnt work

# now going to try transposing

all_df_t <- data.frame(t(all_df))

# damn that worked
# no column names though, but there might be a way to do that

# tried adding row names above to the original data frames but didn't work
# maybe we can transpose the original data frames, add col names, and then combine

cross_df_t <- data.frame(t(cross_df))

for (i in seq_along(cross_df_t)){
  colnames(cross_df_t[[i]]) <- eoae_cross$Name
}

# doesn't seem to be working right now, will try again some other time

# for now, going to export the full data frame into a csv
library(here)

write.csv(all_df_t, "G:/Data Analysis/SomefinFishE/FISHE_tests/stock_assessment/eoae_df.csv", row.names = FALSE)

```

