---
title: "Baseline"
output: html_document
---

Baseline Model: No management and no climate change


Packages:
```{r packages, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
```


Define the PT surplus production model:
```{r pt_model}

# Define the function
pt <- function(B_t, r, K, p, H){
  B_t <- B_t + (
    ((r/p) * B_t) *
      (1-((B_t/K) ^ (p)))
    ) - H
  return(B_t)
}

```

Under no management we are assuming that the harvest (H term of pt model) would be the given by F_oa*B_t
Where: 
 - F_oa = fishing mortality at open access (defined as 0.3*Bmsy from Gaines et al 2018)
 - B_t = biomass at time t

Define the amount of harvest equation (the H term of the pt model): 
```{r mortality}
F_oa <- function(r,p){
  (r/p) * (1-
             ((0.3 ^ (p))/
                ((p+1) ^ (1+p)))
           )
}

```


Define parameters:
```{r parameters}
#Define initial parameters:
#Note these values of r are made up - not actually reflective of slow vs fast growing species; need to find this still
r_slow<- 0.1 #intrinsic growth rate for slow-growing species()
r_med <- 0.5 #intrinsic growth rate for medium-growing species ()
r_fast <- 0.8 #intrinsic growth rate for fast-growing species ()

K <- 10000 #carrying capacity (metric tons)
p <- 0.2 #shape parameter 


B0_open <- 0.1*K #Assume initial biomass is being fished at open access

B_t <- B0_open #at time 1 B_t = B0


```


Time Loop (Slow):
```{r slow}
# Define timescale (t)
tyears <- 100

#Find F_oa
F_slow <- F_oa(r=r_slow, p=p)

#Reset B_t
B_t <- B0_open

#Looped pt model:
for(t in 2:tyears){
  B_t[t] <- pt(B_t = B_t[t-1], r = r_slow, K = K, p = p, H = F_slow*B_t[t-1])
}

plot(B_t)

# save results in a data frame

# create a time vector
time <- c(1:100)

# create a data frame with time vector
results_slow <- as.data.frame(time)

# add model loop result vector to data frame
results_slow$B_t <- B_t

```


Time Loop (Medium):
```{r medium}
# Define timescale (t)
tyears <- 100

#Find F_oa
F_med <- F_oa(r=r_med, p=p)

#Reset B_t
B_t <- B0_open

#Looped pt model:
for(t in 2:tyears){
  B_t[t] <- pt(B_t = B_t[t-1], r = r_med, K = K, p = p, H = F_med*B_t[t-1])
}

plot(B_t)

# save results in a data frame

# create a data frame with time vector
results_medium <- as.data.frame(time)

# add model loop result vector to data frame
results_medium$B_t <- B_t

```


Time Loop (Fast):
```{r fast}
# Define timescale (t)
tyears <- 100

#Find F_oa
F_fast <- F_oa(r=r_fast, p=p)

#Reset B_t
B_t <- B0_open

#Looped pt model:
for(t in 2:tyears){
  B_t[t] <- pt(B_t = B_t[t-1], r = r_fast, K = K, p = p, H = F_fast*B_t[t-1])
}

plot(B_t)

# save results in a data frame

# create a data frame with time vector
results_fast <- as.data.frame(time)

# add model loop result vector to data frame
results_fast$B_t <- B_t
```



