---
title: "Purrr exploration"
author: "Gracie White"
date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#{.tabset}

##Setup
```{r}
library(tidyverse)
library(purrr)
library(repurrrsive)
```

##Practice
Here's a random and totally made up thing to test purrr with cross:
```{r basic_purrr}

#Create three lists:
x <- list(1,10,100)
y <- list(1,2,3)
z <- list(5,50,500)

#Create a master list 
data <- list(
  x = x,
  y = y,
  z = z
)

test <- function(x,y,z){
  result <- x+y+z
}

test_cross <- data %>%
  cross() 

results_test2 <- list()

for(i in 1:27){
  results_test2[i] <- test(x = test_cross[[i]]$x, y = test_cross[[i]]$y, z = test_cross[[i]]$z)
}

```
Unsure how to use this with purrr but it works if you loop over the crossed dataframe.

##Model
Code for the model:
```{r model-function}

sim_fishery <- function(b, f, r, r_s, p, k, years){

  results <- data.frame(
    b = rep(NA, years), c = rep(NA, years), 
    year = 1:years, r = rep(NA, years), r_s = rep(NA, years), f = rep(NA, years)) #Setup the results dataframe where the outputs will be writen for however many years our experiment is running
  
  #Set the initial result for the outputs in year 1
  results$b[1] = b
  results$c[1] = f * b
  results$r[1] = r
  results$r_s[1] = r_s
  results$f[1] = f
  
  #Loop the model over the specified number of years
  for (t in 2:years) {
    
    results$c[t] = results$b[t-1] * f #define catch
    results$b[t] = results$b[t-1] + ((results$r[t-1] / p)*results$b[t-1]*(1 - ((results$b[t-1]/k)
                                                                              ^ p)))-results$c[t] #pt model
    results$r[t] = results$r[1] * (1 + (r_s*(t-1))) #climate model
    results$r_s[t] = r_s
    results$f[t] = f
   } 
  
  return(results)
}




```

##Simple Test

Set up the initial lists and use cross to create a master list of experiments:
```{r setup-test1}

# Starting really simple first - create a list of 3 numbers for each of the inputs in the model:
b <- list(1000, 5000, 10000)
r <- list(0.015, 0.80, 1.15)
r_s <- list(-0.015, 0, 0.02)
f <- list(0.1, 0.3, 0.6)
# I want to hold p, k, and years constant but not repeat combinations - only need to list these once
p <- 0.2
k <- 10000
years <- 50

#Create the master list of inputs
inputs <- list(
  b=b,
  r=r,
  r_s=r_s,
  f=f,
  p=p,
  k=k,
  years=years
)

input_cross <- inputs %>% #cross function requires the input to be one big list of things to cross reference
  cross() #the cross function will create lists of all combinations
```

Great - that looks like what we want!!!

Now we need to loop the function over the master list
```{r loop-test1}

#Create the loop over the number of lists in the crossed list input (in this case there are 81 lists)
#What this loop does is apply the sim_fishery function over each of the 81 lists using the combination of 7 inputs inside that list as the input variables for the equation

for(i in 1:81){
  results[[i]] <- sim_fishery(b=input_cross[[i]]$b, r=input_cross[[i]]$r, r_s=input_cross[[i]]$r_s,
                            f=input_cross[[i]]$f, p=input_cross[[i]]$p, k=input_cross[[i]]$k,
                            years=input_cross[[i]]$years)
}

#Note: if you get a "number of items to replace isn't a multiple of replacement" you need to make sure there are double brackets around all the i values in the equation
#Output should be a list of 81 and inside each list are 50 observations (or the number of years specified) for the six different variables being tracked in the function 
```


WOW THIS WORKS!!!!!!!!!!!!!!!!!!!!!!!!!!!!

Here's what we did:
 - Created a master list that contained lists of each variable we wanted to test in the model.   
 - Used the cross() function to turn that into a long master list of all possible combinations.   
 - Looped our function over the master list (crossed list) where each list contained all the necessary input variables for one run of the model.  

##More Complex Test

To run a more complex test we'll use a longer initial list. The previous test used a list of 3 for b, r, r_s, and f. This time we'll use a list of 10 - varying b and f only.

```{r setup-test2}

#Create the master list of input variables that will feed into the cross() function
# If the input doesn't vary in the different experiments just put one value NOT A LIST
##Note: it isn't necessary to specify n_experiments because we only need one value for constant parameters
experiment <- list(
  b = seq(1000, 10000, 1000),
  r = 0.2,
  r_s = 0,
  f = seq(0.01, 0.91, 0.1),
  p = 0.2,
  k = 10000,
  years = 50)

#Use cross() to create a master list
experiment_cross <- experiment %>%
  cross()
#Creates a list of 100 'experiments' inside each experiment are the seven parameters required to run the model
```


Loop the function where each of the lists in experiment_cross is one experiment with all the necessary input parameters to run the model
```{r loop-test2}
#Set the 1:100 based on the number of lists within experiment_cross() 
for(i in 1:100){
  results[[i]] <- sim_fishery(b=experiment_cross[[i]]$b, r=experiment_cross[[i]]$r,
                              r_s=experiment_cross[[i]]$r_s, f=experiment_cross[[i]]$f, 
                              p=experiment_cross[[i]]$p, k=experiment_cross[[i]]$k,
                              years=experiment_cross[[i]]$years)
}
```

This does what we expect - the first 10 lists have biomass 1000-10000 by 1000 and f=0.01 for all of them. Then the next 10 experiments use the same repeating biomass scale with f=0.11 etc. 











