---
title: "analysis"
author: "Sara Orofino"
date: "12/2/2019"
output: html_document
---

#{.tabset}

##Setup

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Packages
library(tidyverse)
library(here)

#Data
rep20c <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep20_clim.csv"))
rep20 <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep20_noclim.csv"))
rep15c <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep15_clim.csv"))
rep15 <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep15_noclim.csv"))
rep10c <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep10_clim.csv"))
rep10 <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep10_noclim.csv"))
rep5c <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep5_clim.csv"))
rep5 <- read_csv(file=file.path(here(),"/FISHE_tests/stock_assessment_new/catch_tests/csv_results/rep5_noclim.csv"))


```


##Rep20

#Decision Calculation
 - Filter four categories of climate change
    - Most extreme negative 0.01767 (1.7% decrease per year)
    - Mid-range negative 0.0967 (0.97% decrease per year)
    - Lower-range negative 0.00167 (0.17% decrease per year)
    - Mid-range positive 0.01033 (1.03% increase per year)
 - Group simulations by error percentage and life history
 - Count the number of times the model chose a ratio that led the manager to make the wrong decision
 
```{r wrangle-20}
#Sequence of r_s to choose categories:
r_s = seq(-0.01767, 0.01623, 0.002)

rep20c_edit <- rep20c %>%
  filter(r_s == -0.01767 | r_s == -0.00967 | r_s == -0.00167 | r_s == 0.01033) %>% 
  group_by(error, r_0, r_s, correct_decision) %>% 
  tally()
```




Probably gonna need to do this for just 10 and 5 years