---
title: "error_noclim"
author: "Sara Orofino"
date: "1/9/2020"
output: html_document
---
#{.tabset}
```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(RColorBrewer)
```

##Data
Need to compare the new error simualtions with no climate change to perfect management and perfect management given FISHE to see what HCRs work.

Read in data:
```{r data, message=FALSE, warning=FALSE, include=FALSE}
perfect <- read_csv(file=file.path(here(),"/tests/perfect_management/csv_results/perfect_noclim.csv"))
perfect_fishe <- read_csv(file=file.path(here(),"/Results/error/perfect_fishe_noclim.csv"))
error <- read_csv(file=file.path(here(),"/Results/error/error_noclim.csv"))
error_hcrs <- read_csv(file=file.path(here(),"/Results/error/error_noclim_morehcrs.csv"))
```

Want to graph biomass and catch over time for perfect, perfect given FISHE and error at the different HCRs to see which ones work

First let's separate by HCRs:
```{r group-by-hcrs, include=FALSE}
#For perfect given FISHE:
hcr2 <- perfect_fishe %>% 
  filter(hcr == 0.80)

hcr25 <- perfect_fishe %>% 
  filter(hcr == 0.75)

hcr3 <- perfect_fishe %>% 
  filter(hcr == 0.70)

hcr35 <- perfect_fishe %>% 
  filter(hcr == 0.65)

hcr4 <- perfect_fishe %>% 
  filter(hcr == 0.6)

hcr45 <- perfect_fishe %>% 
  filter(hcr == 0.55)

hcr5 <- perfect_fishe %>% 
  filter(hcr == 0.5)

#With error:
err2 <- error %>% 
  filter(hcr == 0.80)

err25 <- error %>% 
  filter(hcr == 0.75)

err3 <- error %>% 
  filter(hcr == 0.70)

err35 <- error %>% 
  filter(hcr == 0.65)

err4 <- error %>% 
  filter(hcr == 0.60)

err45 <- error %>% 
  filter(hcr == 0.55)

err5 <- error %>% 
  filter(hcr == 0.50)
```

##20% Reduction 
First need to get a subset that's easier to graph. Since b0 = 1500 and r = 0.1 is probably the most likely to not do well I'll subset for that.  
```{r wrangle-20, include=FALSE}
#perfect management:
sub_perf <- perfect %>%
  filter(id == 1)

#perfect with fishe:
sub_fishe <- hcr2 %>%
  filter(id == 145)

#error 0.1:
sub_1 <- err2 %>% 
  filter(id == 433)
#error 0.3:
sub_3 <- err2 %>% 
  filter(id == 457)
#error 0.5:
sub_5 <- err2 %>% 
  filter(id == 481)
```

Graph biomass and catch over time:  
```{r biomass-graphs-20, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_20 <- ggplot(sub_perf, aes(x=year, y=b, color = "a")) +
  geom_line() +
  geom_line(data = sub_fishe, aes(x=year, y=b, color = "b")) +
  geom_line(data = sub_1, aes(x=year, y=b, color = "c")) +
  geom_line(data = sub_3, aes(x=year, y=b, color = "d")) +
  geom_line(data = sub_5, aes(x=year, y=b, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) +
  labs(x = "Year", y = "Biomass", title = "20% HCR") +
  theme_bw()

biomass_20

#Catch over time:
catch_20 <- ggplot(sub_perf, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data = sub_fishe, aes(x=year, y=c, color = "b")) +
  geom_line(data = sub_1, aes(x=year, y=c, color = "c")) +
  geom_line(data = sub_3, aes(x=year, y=c, color = "d")) +
  geom_line(data = sub_5, aes(x=year, y=c, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Catch", title = "20% HCR") + 
  theme_bw()

catch_20

```

##25% Reduction

Subset for b0 = 1500 and r = 0.1; perfect management won't change so just need to subset for perfect given FISHE and the error tests.        
```{r wrangle-25, include=FALSE}

#perfect with fishe:
sub2_fishe <- hcr25 %>%
  filter(id == 121)

#error 0.1:
sub2_1 <- err25 %>% 
  filter(id == 361)
#error 0.3:
sub2_3 <- err25 %>% 
  filter(id == 385)
#error 0.5:
sub2_5 <- err25 %>% 
  filter(id == 409) %>% 
  filter(year < 16)
```

Graph biomass and catch over time:  
```{r biomass-graphs-25, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_25 <- ggplot(sub_perf, aes(x=year, y=b, color = "a")) +
  geom_line() +
  geom_line(data = sub2_fishe, aes(x=year, y=b, color = "b")) +
  geom_line(data = sub2_1, aes(x=year, y=b, color = "c")) +
  geom_line(data = sub2_3, aes(x=year, y=b, color = "d")) +
  geom_line(data = sub2_5, aes(x=year, y=b, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) +
  labs(x = "Year", y = "Biomass", title = "25% HCR") +
  theme_bw()

biomass_25

#Catch over time:
catch_25 <- ggplot(sub_perf, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data = sub2_fishe, aes(x=year, y=c, color = "b")) +
  geom_line(data = sub2_1, aes(x=year, y=c, color = "c")) +
  geom_line(data = sub2_3, aes(x=year, y=c, color = "d")) +
  geom_line(data = sub2_5, aes(x=year, y=c, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Catch", title = "25% HCR") + 
  theme_bw()

catch_25

```


##30% Reduction

Subset for b0 = 1500 and r = 0.1; perfect management won't change so just need to subset for perfect given FISHE and the error tests.          
```{r wrangle-30, include=FALSE}

#perfect with fishe:
sub3_fishe <- hcr3 %>%
  filter(id == 97)

#error 0.1:
sub3_1 <- err3 %>% 
  filter(id == 289)
#error 0.3:
sub3_3 <- err3 %>% 
  filter(id == 313)
#error 0.5:
sub3_5 <- err3 %>% 
  filter(id == 337) %>% 
  filter(year < 16)
```

Graph biomass and catch over time:    
```{r biomass-graphs-30, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_3 <- ggplot(sub_perf, aes(x=year, y=b, color = "a")) +
  geom_line() +
  geom_line(data = sub3_fishe, aes(x=year, y=b, color = "b")) +
  geom_line(data = sub3_1, aes(x=year, y=b, color = "c")) +
  geom_line(data = sub3_3, aes(x=year, y=b, color = "d")) +
  geom_line(data = sub3_5, aes(x=year, y=b, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) +
  labs(x = "Year", y = "Biomass", title = "30% HCR") +
  theme_bw()

biomass_3

#Catch over time:
catch_3 <- ggplot(sub_perf, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data = sub3_fishe, aes(x=year, y=c, color = "b")) +
  geom_line(data = sub3_1, aes(x=year, y=c, color = "c")) +
  geom_line(data = sub3_3, aes(x=year, y=c, color = "d")) +
  geom_line(data = sub3_5, aes(x=year, y=c, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Catch", title = "30% HCR") + 
  theme_bw()

catch_3

```


##35% Reduction

Subset for b0 = 1500 and r = 0.1; perfect management won't change so just need to subset for perfect given FISHE and the error tests.          
```{r wrangle-35, include=FALSE}

#perfect with fishe:
sub35_fishe <- hcr35 %>%
  filter(id == 73)

#error 0.1:
sub35_1 <- err35 %>% 
  filter(id == 217)
#error 0.3:
sub35_3 <- err35 %>% 
  filter(id == 241) %>% 
  filter(year < 6)
#error 0.5:
sub35_5 <- err35 %>% 
  filter(id == 265)
```

Graph biomass and catch over time:    
```{r biomass-graphs-35, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_35 <- ggplot(sub_perf, aes(x=year, y=b, color = "a")) +
  geom_line() +
  geom_line(data = sub35_fishe, aes(x=year, y=b, color = "b")) +
  geom_line(data = sub35_1, aes(x=year, y=b, color = "c")) +
  geom_line(data = sub35_3, aes(x=year, y=b, color = "d")) +
  geom_line(data = sub35_5, aes(x=year, y=b, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) +
  labs(x = "Year", y = "Biomass", title = "35% HCR") +
  theme_bw()

biomass_35

#Catch over time:
catch_35 <- ggplot(sub_perf, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data = sub35_fishe, aes(x=year, y=c, color = "b")) +
  geom_line(data = sub35_1, aes(x=year, y=c, color = "c")) +
  geom_line(data = sub35_3, aes(x=year, y=c, color = "d")) +
  geom_line(data = sub35_5, aes(x=year, y=c, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Catch", title = "35% HCR") + 
  theme_bw()

catch_35

```

##40% Reduction

Subset for b0 = 1500 and r = 0.1; perfect management won't change so just need to subset for perfect given FISHE and the error tests.          
```{r wrangle-40, include=FALSE}

#perfect with fishe:
sub4_fishe <- hcr4 %>%
  filter(id == 49)

#error 0.1:
sub4_1 <- err4 %>% 
  filter(id == 145)
#error 0.3:
sub4_3 <- err4 %>% 
  filter(id == 169)
#error 0.5:
sub4_5 <- err4 %>% 
  filter(id == 193)
```

Graph biomass and catch over time:    
```{r biomass-graphs-40, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_4 <- ggplot(sub_perf, aes(x=year, y=b, color = "a")) +
  geom_line() +
  geom_line(data = sub4_fishe, aes(x=year, y=b, color = "b")) +
  geom_line(data = sub4_1, aes(x=year, y=b, color = "c")) +
  geom_line(data = sub4_3, aes(x=year, y=b, color = "d")) +
  geom_line(data = sub4_5, aes(x=year, y=b, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) +
  labs(x = "Year", y = "Biomass", title = "40% HCR") +
  theme_bw()

biomass_4

#Catch over time:
catch_4 <- ggplot(sub_perf, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data = sub4_fishe, aes(x=year, y=c, color = "b")) +
  geom_line(data = sub4_1, aes(x=year, y=c, color = "c")) +
  geom_line(data = sub4_3, aes(x=year, y=c, color = "d")) +
  geom_line(data = sub4_5, aes(x=year, y=c, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Catch", title = "40% HCR") + 
  theme_bw()

catch_4

```

##45% Reduction

Subset for b0 = 1500 and r = 0.1; perfect management won't change so just need to subset for perfect given FISHE and the error tests.          
```{r wrangle-45, include=FALSE}

#perfect with fishe:
sub45_fishe <- hcr45 %>%
  filter(id == 25)

#error 0.1:
sub45_1 <- err45 %>% 
  filter(id == 73)
#error 0.3:
sub45_3 <- err45 %>% 
  filter(id == 97)
#error 0.5:
sub45_5 <- err45 %>% 
  filter(id == 121)
```

Graph biomass and catch over time:    
```{r biomass-graphs-45, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_45 <- ggplot(sub_perf, aes(x=year, y=b, color = "a")) +
  geom_line() +
  geom_line(data = sub45_fishe, aes(x=year, y=b, color = "b")) +
  geom_line(data = sub45_1, aes(x=year, y=b, color = "c")) +
  geom_line(data = sub45_3, aes(x=year, y=b, color = "d")) +
  geom_line(data = sub45_5, aes(x=year, y=b, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) +
  labs(x = "Year", y = "Biomass", title = "45% HCR") +
  theme_bw()

biomass_45

#Catch over time:
catch_45 <- ggplot(sub_perf, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data = sub45_fishe, aes(x=year, y=c, color = "b")) +
  geom_line(data = sub45_1, aes(x=year, y=c, color = "c")) +
  geom_line(data = sub45_3, aes(x=year, y=c, color = "d")) +
  geom_line(data = sub45_5, aes(x=year, y=c, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Catch", title = "45% HCR") + 
  theme_bw()

catch_45

```

##50% Reduction

Subset for b0 = 1500 and r = 0.1; perfect management won't change so just need to subset for perfect given FISHE and the error tests.          
```{r wrangle-50, include=FALSE}

#perfect with fishe:
sub5_fishe <- hcr5 %>%
  filter(id == 1)

#error 0.1:
sub5_1 <- err5 %>% 
  filter(id == 1)
#error 0.3:
sub5_3 <- err5 %>% 
  filter(id == 25)
#error 0.5:
sub5_5 <- err5 %>% 
  filter(id == 49)
```

Graph biomass and catch over time:    
```{r biomass-graphs-50, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_5 <- ggplot(sub_perf, aes(x=year, y=b, color = "a")) +
  geom_line() +
  geom_line(data = sub5_fishe, aes(x=year, y=b, color = "b")) +
  geom_line(data = sub5_1, aes(x=year, y=b, color = "c")) +
  geom_line(data = sub5_3, aes(x=year, y=b, color = "d")) +
  geom_line(data = sub5_5, aes(x=year, y=b, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) +
  labs(x = "Year", y = "Biomass", title = "50% HCR") +
  theme_bw()

biomass_5

#Catch over time:
catch_5 <- ggplot(sub_perf, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data = sub5_fishe, aes(x=year, y=c, color = "b")) +
  geom_line(data = sub5_1, aes(x=year, y=c, color = "c")) +
  geom_line(data = sub5_3, aes(x=year, y=c, color = "d")) +
  geom_line(data = sub5_5, aes(x=year, y=c, color = "e")) +
  scale_color_manual(name = "", breaks = c("a", "b", "c", "d", "e"), 
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'), 
                     labels = c("Perfect Management", "Perfect given FISHE", "FISHE with 10% Error", "FISHE with 30% Error", "FISHE with 50% Error")) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Catch", title = "50% HCR") + 
  theme_bw()

catch_5

```


##HCR Table

Make a table with different errors as the rows and the number of simulations that went over the limit (with error) at each of the different HCRs  

```{r table-wrangle}

#I think I want to make two tables split by 10-30% reduction and then 35-50% reduction
hcr_10 <- error_hcrs %>%
  filter(hcr >= 0.7)
hcr_35 <- error_hcrs %>%
  filter(hcr <= 0.65)

#First I'm interested in just knowing how many of the 648 fisheries were closed by year 100 at different error levels:
##10-30%
hcr10_100 <- hcr_10 %>% 
  filter(year == 100) %>% 
  mutate(closed = ifelse(f_ratio == 0, "yes", "no")) %>% 
  group_by(hcr, error) %>% 
  count(closed) %>% 
  spread(key = "closed", value = "n") %>% 
  nest(yes, no, .key = "closed") %>% 
  pivot_wider(names_from = hcr,
              values_from = closed) %>% 
  unnest()
#create a list of column names
col_names <- c("error", "0.7yes", "0.7no", "0.75yes", "0.75no",
               "0.8yes", "0.8no", "0.85yes", "0.85no", "0.9yes", "0.9no")
#Rename columns:
colnames(hcr10_100) <- col_names
#Change NA to zero:
hcr10_100[is.na(hcr10_100)] <- 0


##35-50%
hcr35_100 <- hcr_35 %>% 
  filter(year == 100) %>% 
  mutate(closed = ifelse(f_ratio == 0, "yes", "no")) %>% 
  group_by(hcr, error) %>% 
  count(closed) %>% 
  spread(key = "closed", value = "n") %>% 
  nest(yes, no, .key = "closed") %>% 
  pivot_wider(names_from = hcr,
              values_from = closed) %>% 
  unnest()
#create a list of column names
col_names2 <- c("error", "0.5yes", "0.5no", "0.55yes", "0.55no",
               "0.6yes", "0.6no", "0.65yes", "0.65no")
#Rename columns:
colnames(hcr35_100) <- col_names2
#Change NA to zero:
hcr35_100[is.na(hcr35_100)] <- 0




# #First need to define what the failure is and group by hcr, id, and error:
# hcr10_counts <- hcr_10 %>% 
#   mutate(over_limit = ifelse(f_ratio_err >= 2, "yes",ifelse(f_ratio_err == 0, "close", "no"))) %>% 
#   group_by(hcr, error) %>% 
#   count(over_limit) %>% 
#   spread(key = "over_limit", value = "n") %>% 
#   nest(close, no, yes, .key = 'value_col') %>% 
#   pivot_wider(names_from = hcr,
#               values_from = value_col) %>% 
#   unnest()
# 
# #create a list of column names
# col_names <- c("error", "0.7close", "0.7no", "0.7yes", "0.75close", "0.75no", "0.75yes",
#                "0.8close", "0.8no", "0.8yes", "0.85close", "0.85no", "0.85yes", "0.9close", "0.9no", "0.9yes")
# #Rename columns:
# colnames(hcr10_counts) <- col_names
# #Change NA to zero:
# hcr10_counts[is.na(hcr10_counts)] <- 0
```


Create the tables:  
```{r kable}
library(kableExtra)


```

