---
title: "error_analysis"
author: "Sara Orofino"
date: "12/2/2019"
output: html_document
---

#{.tabset}

##Setup

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Packages
library(tidyverse)
library(here)

#Data
err_rep5c <- read_csv(file=file.path(here(),"/Results/error/error_constant_rep5.csv"))
err_rep5u <- read_csv(file=file.path(here(),"/Results/error/error_updating_rep5.csv"))
err_rep10c <- read_csv(file=file.path(here(),"/Results/error/error_constant_rep10.csv"))
err_rep10u <- read_csv(file=file.path(here(),"/Results/error/error_updating_rep10.csv"))

```


##Decision Calculation
 - Filter negative climate change 
 - Filter for assessment years ONLY
 - Group simulations by error percentage
 - Count the number of times the model chose a ratio that led the manager to make the wrong decision

Rep5 - Updating
Do some basic data wrangling for 5 year intervals where Fmsy updating with climate change:
  - Look at all negative climate change scenarios
  - Look at ONLY assessments where a decision was actually made (filter out times when the fishery was closed)
  - Group by error percentage 
```{r wrangle-5u-basic}
#Assessment years:
assess_5 <- seq(5,100,5)

#Find the proportion of wrong decisions excluding assessments where the fishery was closed 
rep5u_no <- err_rep5u %>%
  filter(r_s <= 0) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  filter(decision_made == "yes") %>% 
  group_by(error, correct_decision) %>% 
  tally() %>% 
  rename("count_5u" = n) %>% 
  spread(key = "correct_decision", value = "count_5u") %>%
  mutate(total_decisions_made = sum(no + yes)) %>% 
  mutate(prop_no = no/total_decisions_made)

#Now I want to transform the error into factors
rep5u_no$error <- as.factor(rep5u_no$error)

```


Now I want to see how many "fails" were included in each error category
```{r 5u-fails}

#Find the proportion of yes, no, and fail for each error category
rep5u_fail <- err_rep5u %>% 
  filter(r_s <= 0) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(error, correct_decision) %>% 
  tally() %>% 
  rename("count_5u" = n) %>% 
  spread(key = "correct_decision", value = "count_5u") %>% 
  mutate(total_decisions = sum(yes + no + fail)) %>% 
  mutate(prop_fail = fail / total_decisions)

#Now I want to transform the error into factors
rep5u_fail$error <- as.factor(rep5u_fail$error)
```



Rep10 - Updating
Data wrangling for 10 year intervals where Fmsy is updating with climate change:
```{r wrangle-10u-basic}

#Assessment years:
assess_10 <- seq(10,100,10)

#Find the proportion of wrong decisions excluding assessments where the fishery was closed 
rep10u_no <- err_rep10u %>%
  filter(r_s <= 0) %>% 
  filter(year == 1 | year %in% assess_10) %>% 
  filter(decision_made == "yes") %>% 
  group_by(error, correct_decision) %>% 
  tally() %>% 
  rename("count_10u" = n) %>% 
  spread(key = "correct_decision", value = "count_10u") %>% 
  mutate(total_decisions_made = sum(no + yes)) %>% 
  mutate(prop_no = no/total_decisions_made)

#Now I want to transform the error into factors
rep10u_no$error <- as.factor(rep10u_no$error)


```

Now I want to see how many "fails" were included in each error category
```{r 10u-fails}

#Find the proportion of yes, no, and fail for each error category
rep10u_fail <- err_rep10u %>% 
  filter(r_s <= 0) %>% 
  filter(year == 1 | year %in% assess_10) %>% 
  group_by(error, correct_decision) %>% 
  tally() %>% 
  rename("count_10u" = n) %>% 
  spread(key = "correct_decision", value = "count_10u") %>% 
  mutate(total_decisions = sum(yes + no + fail)) %>% 
  mutate(prop_fail = fail / total_decisions)

#Now I want to transform the error into factors
rep10u_fail$error <- as.factor(rep10u_fail$error)

```

##Table

Proportion of yes/no/fail for 5 year updating Fmsy at the three different errors:
```{r rep5-table}
library(kableExtra)

rep5 <- err_rep5u %>% 
  filter(r_s <= 0) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(error, correct_decision) %>% 
  tally() %>% 
  rename("count_5u" = n) %>% 
  spread(key = "correct_decision", value = "count_5u") %>% 
  mutate(total_assessments = sum(yes + no + fail)) %>% 
  mutate(decisions_made = sum(yes + no)) %>% 
  mutate(prop_fail = round(fail / total_assessments, digits = 3)) %>% 
  mutate(prop_no = round(no / decisions_made, digits = 3)) %>% 
  mutate(prop_yes = round(yes / decisions_made, digits = 3)) %>% 
  select(error, total_assessments, fail, prop_fail, decisions_made, yes, prop_yes, no, prop_no)

rep5_table <- kable(rep5, col.names = c("Error", "Number of Assessments", "Fail", "Proportion of Failures", "Number of Decisions Made",
                                        "Number of Yes", "Proportion of Yes", "Number of No", "Proportion of No")) %>% 
  kable_styling(bootstrap_options = c("striped", "bordered", "condensed"), full_width = F) %>% 
  row_spec(0, align = "c", font_size = 10) %>% 
  row_spec(1, font_size = 10) %>% 
  row_spec(2, font_size = 10) %>% 
  row_spec(3, font_size = 10)

rep5_table
```

Proportion of yes/no/fail for 10 year updating Fmsy at the three different errors:
```{r rep10-table}
rep10 <- err_rep10u %>% 
  filter(r_s <= 0) %>% 
  filter(year == 1 | year %in% assess_10) %>% 
  group_by(error, correct_decision) %>% 
  tally() %>% 
  rename("count_10u" = n) %>% 
  spread(key = "correct_decision", value = "count_10u") %>% 
  mutate(total_assessments = sum(yes + no + fail)) %>% 
  mutate(decisions_made = sum(yes + no)) %>% 
  mutate(prop_fail = round(fail / total_assessments, digits = 3)) %>% 
  mutate(prop_no = round(no / decisions_made, digits = 3)) %>% 
  mutate(prop_yes = round(yes / decisions_made, digits = 3)) %>% 
  select(error, total_assessments, fail, prop_fail, decisions_made, yes, prop_yes, no, prop_no)

rep10_table <- kable(rep10, col.names = c("Error", "Number of Assessments", "Fail", "Proportion of Failures", "Number of Decisions Made",
                                        "Number of Yes", "Proportion of Yes", "Number of No", "Proportion of No")) %>% 
  kable_styling(bootstrap_options = c("striped", "bordered", "condensed"), full_width = F) %>% 
  row_spec(0, align = "c", font_size = 10) %>% 
  row_spec(1, font_size = 10) %>% 
  row_spec(2, font_size = 10) %>% 
  row_spec(3, font_size = 10)

rep10_table
```


##Visualizations

Experiment with a few ways of visualizing this data

Rep5

First try proportion of failures on the y-axis with error categories on the x-axis for updating Fmsy
```{r rep5-viz1}

fail5 <- ggplot(rep5u_no, aes(x = error, y= prop_no)) +
  geom_point(aes(color = "No")) + 
  geom_point(aes(x = error, y = prop_fail, color = "Fail"), data = rep5u_fail) + 
  scale_color_manual(breaks = c("No", "Fail"), values = c("midnightblue", "firebrick4")) +
  labs(x = "Error", y = "Proportion") +
  guides(color=guide_legend(title=NULL)) +
  theme_bw() 

fail5


```

Rep10

First try proportion of failures on the y-axis with error categories on the x-axis for updating Fmsy
```{r rep10-viz1}

fail10 <- ggplot(rep10u_no, aes(x = error, y= prop_no)) +
  geom_point(aes(color = "No")) + 
  geom_point(aes(x = error, y = prop_fail, color = "Fail"), data = rep10u_fail) + 
  scale_color_manual(breaks = c("No", "Fail"), values = c("midnightblue", "firebrick4")) +
  labs(x = "Error", y = "Proportion") +
  guides(color=guide_legend(title=NULL)) +
  theme_bw() 

fail10

```







