---
title: "error_analysis_hcr30"
author: "Sara Orofino"
date: "1/13/2020"
output: html_document
---

#{.tabset}

##Setup

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Packages
library(tidyverse)
library(here)
library(RColorBrewer)
library(data.table)

#Data
err_rep5u <- read_csv(file=file.path(here(),"/Results/error/error_updating_rep5_hcr30.csv"))
err_rep10u <- read_csv(file=file.path(here(),"/Results/error/error_updating_rep10_hcr30.csv"))
err_rep5c <- read_csv(file=file.path(here(),"/Results/error/error_constant_rep5_hcr30.csv"))
err_rep10c <- read_csv(file=file.path(here(),"/Results/error/error_constant_rep10_hcr30.csv"))


#Comparision of perfect management data
perfect <- read_csv(file=file.path(here(),"/Tests/perfect_management/csv_results/perfect_r0.1.csv"))
perfect_fishe <- read_csv(file=file.path(here(),"/Results/error/perfect_updating_rep5_hcr30.csv"))

```

##Cumulative Yield Example

###Slow Growing
Initial Conditions of Experiment:
  - b0 = 4000
  - r = 0.2 
  - r_s = -0.01767
  - error = 0.1

Perfect Management: ID = 8
Perfect given FISHE: ID = 5
Error: ID = 5, 413, 821
```{r error, include=FALSE}
#Find an error simulation at climate of -0.01767 that doesn't collapse
err <- err_rep5u %>% 
  filter(r_s == -0.01767) %>% 
  filter(c != 0) %>% 
  filter(r_0 == 0.2)
#Use experiment 5 

#Find the experiment with same r0 and r_s for 0.3 error and 0.5 error 
err_3 <- err_rep5u %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 == 0.2) %>% 
  filter(error == 0.3)
#413
err_5 <- err_rep5u %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 == 0.2) %>% 
  filter(error == 0.5)
#821
```


```{r cumulative-yield-slow, echo=FALSE}

#Calculate cumulative yield under perfect management
perfect_slow <- perfect %>% 
  filter(id == 8)

yield_perfect_slow = sum(perfect_slow$c)
yield_perfect_slow

#Calculate cumulative yield under perfect management given FISHE
fishe_slow <- perfect_fishe %>% 
  filter(id == 5)

yield_fishe_slow = sum(fishe_slow$c)
yield_fishe_slow

#Calculate cumulative yield in error simulations:
error1_slow <- err_rep5u %>% 
  filter(id == 5) 
error3_slow <- err_rep5u %>% 
  filter(id == 413) 
error5_slow <- err_rep5u %>% 
  filter(id == 821) %>% 
  filter(year < 71)

yield_error1_slow = sum(error1_slow$c)
yield_error3_slow = sum(error3_slow$c)
yield_error5_slow = sum(error5_slow$c)

yield_error1_slow
yield_error3_slow
yield_error5_slow
```

###Fast Growing
Initial Conditions of Experiment:
  - b0 = 4000
  - r = 0.8
  - r_s = -0.01767
  - error = 0.1
  
Perfect Management: ID = 44
Perfect given FISHE: ID = 23
Error: ID = 23, 431, 839  
```{r error-fast, include=FALSE}
#Find the right error experiment to use
err_fast <- err_rep5u %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 == 0.8)
#Use experiment 23

#Find the experiment with same r0 and r_s for 0.3 error and 0.5 error 
err_3f <- err_rep5u %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 == 0.8) %>% 
  filter(error == 0.3)
#431
err_5f <- err_rep5u %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 == 0.8) %>% 
  filter(error == 0.5)
#839
```


```{r cumulative-yield-fast, echo=FALSE}

#Calculate cumulative yield under perfect management
perfect_fast <- perfect %>% 
  filter(id == 44)

yield_perfect_fast = sum(perfect_fast$c)
yield_perfect_fast

#Calculate cumulative yield under perfect management given FISHE
fishe_fast <- perfect_fishe %>% 
  filter(id == 23)

yield_fishe_fast = sum(fishe_fast$c)
yield_fishe_fast

#Calculate cumulative yield in error simulation
error1_fast <- err_rep5u %>% 
  filter(id == 23)
error3_fast <- err_rep5u %>% 
  filter(id == 431)
error5_fast <- err_rep5u %>% 
  filter(id == 839) 

yield_error_fast1 = sum(error1_fast$c)
yield_error_fast3 = sum(error3_fast$c)
yield_error_fast5 = sum(error5_fast$c)

yield_error_fast1
yield_error_fast3
yield_error_fast5

```



##Slow Comparison Graph

Graph biomass and catch over time for perfect management, perfect given FISHE, and the error simulation:
```{r biomass-graphs-slow, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_slow <- ggplot(perfect_slow, aes(x=year, y=b)) + 
  geom_line(aes(color = "a")) + 
  geom_line(data = fishe_slow, aes(x=year, y=b, color = "b")) +
  geom_line(data =error1_slow, aes(x=year, y=b, color = "c")) +
  geom_line(data =error3_slow, aes(x=year, y=b, color = "d")) +
  geom_line(data =error5_slow, aes(x=year, y=b, color = "e")) +  
  scale_color_manual(name = '', breaks = c("a","b", "c", "d", "e"),
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'),
                     labels = c("Perfect Management", "Perfect with FISHE", "FISHE with 10% Error", "FISHE with 30% Error",
                                "FISHE with 50% Error")) +
  scale_y_continuous(expand = c(0,0), limits = c(2900,5450), breaks = seq(3000,5500,500)) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Biomass") +
  theme_bw()

biomass_slow

#Catch over time:
catch_slow <- ggplot(perfect_slow, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data=fishe_slow, aes(x=year, y=c, color = "b")) +
  geom_line(data=error1_slow, aes(x=year, y=c, color = "c")) +
  geom_line(data =error3_slow, aes(x=year, y=c, color = "d")) +
  geom_line(data =error5_slow, aes(x=year, y=c, color = "e")) +  
  scale_color_manual(name = '', breaks = c("a","b", "c", "d", "e"),
                     values = c("darkgreen",'navy','gold2', 'darkorange2', 'firebrick4'),
                     labels = c("Perfect Management", "Perfect with FISHE", "FISHE with 10% Error", "FISHE with 30% Error",
                                "FISHE with 50% Error")) +
  scale_y_continuous(expand = c(0,0), limits = c(100,720), breaks = seq(100,700,100)) +
  scale_x_continuous(expand = c(0,0.5), breaks = seq(0,100,5)) + 
  labs(x = "Year", y = "Catch") + 
  theme_bw()

catch_slow

```

##Fast Comparison Graph

Graph biomass and catch over time for perfect management, perfect given FISHE, and the error simulation:
```{r biomass-graphs-fast, echo=FALSE, warning=FALSE}

#Biomass over time:
biomass_fast <- ggplot(perfect_fast, aes(x=year, y=b)) + 
  geom_line(aes(color = "a")) + 
  geom_line(data = fishe_fast, aes(x=year, y=b, color = "b")) +
  geom_line(data =error1_fast, aes(x=year, y=b, color = "c")) +
  geom_line(data =error3_fast, aes(x=year, y=b, color = "d")) +
  scale_color_manual(name = '', breaks = c("a","b", "c", "d"),
                     values = c("darkgreen",'navy','gold2', 'darkorange2'),
                     labels = c("Perfect Management", "Perfect with FISHE", "FISHE with 10% Error", "FISHE with 30% Error")) +
  scale_y_continuous(expand = c(0,0), limits = c(2000,5550), breaks = seq(2500,5500,500)) +
  scale_x_continuous(expand = c(0,0.5)) + 
  labs(x = "Year", y = "Biomass") +
  theme_bw()

biomass_fast

#Catch over time:
catch_fast <- ggplot(perfect_fast, aes(x=year, y=c)) + 
  geom_line(aes(color = "a")) +
  geom_line(data=fishe_fast, aes(x=year, y=c, color = "b")) +
  geom_line(data=error1_fast, aes(x=year, y=c, color = "c")) +
  geom_line(data=error3_fast, aes(x=year, y=c, color = "d")) +
  scale_color_manual(name = '', breaks = c("a","b", "c", "d"),
                     values = c("darkgreen",'navy','gold2', 'darkorange2'),
                     labels = c("Perfect Management", "Perfect with FISHE", "FISHE with 10% Error", "FISHE with 30% Error")) +
  scale_y_continuous(expand = c(0,0), limits = c(350,3000), breaks = seq(500,3000,500)) +
  scale_x_continuous(expand = c(0,0.5), breaks = seq(0,100,5)) + 
  labs(x = "Year", y = "Catch") + 
  theme_bw()

catch_fast

```


##Aggregated Cumulative Yields

Cumulative yield patterns for slow and fast show that catch is highest under perfect management and decreases from there in the order we expect (perfect given FISHE, 10% error, 30% error, 50% error)  

Going to try calculating cumulative yields under the most aggressive climate change decline by aggregating slow growing (r = 0.1-0.3), intermediate (r=0.4-0.5), and fast growing (r=0.6-0.8). For now I'm including all three starting biomasses.  


###Slow Growing

Defining slow growing as having growth rates between 0.1 and 0.3. Find cumulative yields for perfect, perfect given FISHE, and the three error scenarios  
  
Steps:  
  - Filter for climate change r_s = -0.01767  
  - Filter for growth rates less than 0.3  
  - Group by Id and calculate cumulative yield (sum of catch for that experiment)  
  - Find the average catch for all the experiments  

UPDATING FMSY: 

```{r slow-yield-calcs-fmsyupdating, include=FALSE}

#Perfect management:
slow_perfect <- perfect %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#Perfect given FISHE:
slow_fishe <- perfect_fishe %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#10% error:
slow_1 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.1) %>%
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c)) 

#30% error:
slow_3 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.3) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#50% error:
slow_5 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.5) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c)) 

##Calculate average catch:
avg_perf_slow <- mean(slow_perfect$cumulative_yield)
avg_fishe_slow <- mean(slow_fishe$cumulative_yield)
avg_slow1 <- mean(slow_1$cumulative_yield)
avg_slow3 <- mean(slow_3$cumulative_yield)
avg_slow5 <- mean(slow_5$cumulative_yield)


##Turn those numbers into a dataframe so you can make a table:
error <- c(0.1, 0.3, 0.5)
sims_s <- c(avg_slow1, avg_slow3, avg_slow5)

yield_slow <- data.frame(error = error, perfect = rep(avg_perf_slow, 3), perfect_fishe = rep(avg_fishe_slow, 3),
                         fishe_sims = sims_s) %>% 
  mutate(percent_perfect = (fishe_sims / perfect_fishe) * 100) #Note this is how close the simulations get to perfect given FISHE


##Calculate the number of "bad outcomes" and the proportion of bad outcomes
#Assessment years:
assess_5 <- seq(5,100,5)

slow1_bad <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.1) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(id, correct_decision) %>% 
  tally() %>% 
  rename("count_5u" = n) %>% 
  spread(key = "correct_decision", value = "count_5u") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(total_decisions = sum(yes + no + fail)) %>% 
  mutate(prop_bad = (fail + no) / total_decisions) 

slow1_badavg <- mean(slow1_bad$prop_bad)


slow3_bad <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.3) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(id, correct_decision) %>% 
  tally() %>% 
  rename("count_5u" = n) %>% 
  spread(key = "correct_decision", value = "count_5u") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(total_decisions = sum(yes + no + fail)) %>% 
  mutate(prop_bad = (fail + no) / total_decisions) 
slow3_badavg <- mean(slow3_bad$prop_bad)

slow5_bad <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.5) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(id, correct_decision) %>% 
  tally() %>% 
  rename("count_5u" = n) %>% 
  spread(key = "correct_decision", value = "count_5u") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(total_decisions = sum(yes + no + fail)) %>% 
  mutate(prop_bad = (fail + no) / total_decisions) 
slow5_badavg <- mean(slow5_bad$prop_bad)

#Add column of prop_bad to the dataframe:
yield_slow$percent_bad <- c(slow1_badavg, slow3_badavg, slow5_badavg)

###Alternative way to make the table:
yield_slow2 <- data.frame(perfect = avg_perf_slow, perfect_fishe = avg_fishe_slow, error_0.1 = avg_slow1,
                          error_0.3 = avg_slow3, error_0.5 = avg_slow5) 

#Need to calculate the percent of perfect for all the columns:
percent_perf <- 100
percent_perf_fishe <- (yield_slow2$perfect_fishe/yield_slow2$perfect) * 100
#note these are calcuting the percent of perfect given FISHE since that's as good as it can possibly be
percent_perf_s0.1 <- (yield_slow2$error_0.1/yield_slow2$perfect_fishe) * 100
percent_perf_s0.3 <- (yield_slow2$error_0.3/yield_slow2$perfect_fishe) * 100
percent_perf_s0.5 <- (yield_slow2$error_0.5/yield_slow2$perfect_fishe) * 100

#Add the row to the dataframe:
yield_slow2 <- add_row(yield_slow2, perfect = percent_perf, perfect_fishe = percent_perf_fishe, error_0.1 = percent_perf_s0.1,
        error_0.3 = percent_perf_s0.3, error_0.5 = percent_perf_s0.5)

#Add row names:
row.names(yield_slow2) = c("cumulative_yield", "percent_perfect")
```

CONSTANT FMSY:  
It's important to compare these updating fmsy results to the constant fmsy results since that seemed really important in other experiments  
Note: I only copied the code for the first type of table but I can easily do the second type of table if that's the preferred one  

```{r slow-yield-calcs-fmsyconstant, include=FALSE}
#Perfect management won't change because it includes updating fmsy as the condition for perfect management

#Perfect given FISHE also doesn't change (I could change the code but I don't think that makes sense in the context of perfect)

#10% error:
slow_1c <- err_rep5c %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.1) %>%
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c)) 

#30% error:
slow_3c <- err_rep5c %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.3) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#50% error:
slow_5c <- err_rep5c %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.5) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c)) 

##Calculate average catch:
avg_perf_slow <- mean(slow_perfect$cumulative_yield)
avg_fishe_slow <- mean(slow_fishe$cumulative_yield)
avg_slow1c <- mean(slow_1c$cumulative_yield)
avg_slow3c <- mean(slow_3c$cumulative_yield)
avg_slow5c <- mean(slow_5c$cumulative_yield)


##Turn those numbers into a dataframe so you can make a table:
error <- c(0.1, 0.3, 0.5)
sims_s <- c(avg_slow1c, avg_slow3c, avg_slow5c)

yield_slowc <- data.frame(error = error, perfect = rep(avg_perf_slow, 3), perfect_fishe = rep(avg_fishe_slow, 3),
                         fishe_sims = sims_s) %>% 
  mutate(percent_perfect = (fishe_sims / perfect_fishe) * 100) #Note this is how close the simulations get to perfect given FISHE

##Calculate the number of "bad outcomes" and the proportion of bad outcomes
#Assessment years:
assess_5 <- seq(5,100,5)

slow1c_bad <- err_rep5c %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.1) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(id, correct_decision) %>% 
  tally() %>% 
  rename("count_5c" = n) %>% 
  spread(key = "correct_decision", value = "count_5c") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>%
  mutate(total_decisions = sum(yes + no)) %>% 
  mutate(prop_bad = no / total_decisions) 
slow1c_badavg <- mean(slow1c_bad$prop_bad)


slow3c_bad <- err_rep5c %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.3) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(id, correct_decision) %>% 
  tally() %>% 
  rename("count_5c" = n) %>% 
  spread(key = "correct_decision", value = "count_5c") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(total_decisions = sum(yes + no + fail)) %>% 
  mutate(prop_bad = (fail + no) / total_decisions) 
slow3c_badavg <- mean(slow3c_bad$prop_bad)

slow5c_bad <- err_rep5c %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 <= 0.3) %>% 
  filter(error == 0.5) %>% 
  filter(year == 1 | year %in% assess_5) %>% 
  group_by(id, correct_decision) %>% 
  tally() %>% 
  rename("count_5c" = n) %>% 
  spread(key = "correct_decision", value = "count_5c") %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) %>% 
  mutate(total_decisions = sum(yes + no + fail)) %>% 
  mutate(prop_bad = (fail + no) / total_decisions) 
slow5c_badavg <- mean(slow5c_bad$prop_bad)

#Add column of prop_bad to the dataframe:
yield_slowc$percent_bad <- c(slow1c_badavg, slow3c_badavg, slow5c_badavg)
```
This dataframe (yield_slowc) indicates that the fisheries get closer to perfect when they don't update their estimates of fmsy. That doesn't make sense with what I would expect, although this could be because this average includes all the runs and not just the ones that made it to year 100. If the fishery is fishing way too high they will have high culumulative yields but they may have collapsed the fishery before the end of the simulation. To check this I will try and add a column that shows percent of bad outcomes as well.  


Make a formal table:  


###Intermediate Growing

Defining intermediate growing as having growth rates between 0.4 and 0.5. Find cumulative yields for perfect, perfect given FISHE, and the three error scenarios    
  
Steps:  
  - Filter for climate change r_s = -0.01767  
  - Filter for growth rates between 0.4 and 0.5    
  - Group by Id and calculate cumulative yield (sum of catch for that experiment)  
  - Find the average catch for all the experiments 
  
```{r int-yield-calcs, include=FALSE}

#Perfect management:
int_perfect <- perfect %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 > 0.3 & r_0 <= 0.5) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#Perfect given FISHE:
int_fishe <- perfect_fishe %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 > 0.3 & r_0 <= 0.5) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#10% error:
int_1 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 > 0.3 & r_0 <= 0.5) %>% 
  filter(error == 0.1) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#30% error:
int_3 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 > 0.3 & r_0 <= 0.5) %>% 
  filter(error == 0.3) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#50% error:
int_5 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 > 0.3 & r_0 <= 0.5) %>% 
  filter(error == 0.5) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

##Calculate average catch:
avg_perf_int <- mean(int_perfect$cumulative_yield)
avg_fishe_int <- mean(int_fishe$cumulative_yield)
avg_int1 <- mean(int_1$cumulative_yield)
avg_int3 <- mean(int_3$cumulative_yield)
avg_int5 <- mean(int_5$cumulative_yield)


##Turn those numbers into a dataframe so you can make a table:
error <- c(0.1, 0.3, 0.5)
sims_i <- c(avg_int1, avg_int3, avg_int5)

yield_int <- data.frame(error = error, perfect = rep(avg_perf_int, 3), perfect_fishe = rep(avg_fishe_int, 3),
                         fishe_sims = sims_i) %>% 
  mutate(percent_perfect = (fishe_sims / perfect_fishe) * 100) #Note this is how close the simulations get to perfect given FISHE



##Alternative way to make the table:
yield_int2 <- data.frame(perfect = avg_perf_int, perfect_fishe = avg_fishe_int, error_0.1 = avg_int1,
                          error_0.3 = avg_int3, error_0.5 = avg_int5) 

#Need to calculate the percent of perfect for all the columns:
percent_perf <- 100
percent_perf_fishe_i <- (yield_int2$perfect_fishe/yield_int2$perfect) * 100
#note these are calcuting the percent of perfect given FISHE since that's as good as it can possibly be
percent_perf_i0.1 <- (yield_int2$error_0.1/yield_int2$perfect_fishe) * 100
percent_perf_i0.3 <- (yield_int2$error_0.3/yield_int2$perfect_fishe) * 100
percent_perf_i0.5 <- (yield_int2$error_0.5/yield_int2$perfect_fishe) * 100

#Add the row to the dataframe:
yield_int2 <- add_row(yield_int2, perfect = percent_perf, perfect_fishe = percent_perf_fishe_i, error_0.1 = percent_perf_i0.1,
        error_0.3 = percent_perf_i0.3, error_0.5 = percent_perf_i0.5)

#Add row names:
row.names(yield_int2) = c("cumulative_yield", "percent_perfect")
```

Make a formal table:  



###Fast Growing

Defining fast growing as having growth rates of 0.6 or greater. Find cumulative yields for perfect, perfect given FISHE, and the three error scenarios      
  
Steps:  
  - Filter for climate change r_s = -0.01767  
  - Filter for growth rates greater than 0.6      
  - Group by Id and calculate cumulative yield (sum of catch for that experiment)  
  - Find the average catch for all the experiments 
  
```{r fast-yield-calcs, include=FALSE}

#Perfect management:
fast_perfect <- perfect %>% 
  filter(r_s == -0.01767) %>% 
  filter(r_0 >= 0.6) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#Perfect given FISHE:
fast_fishe <- perfect_fishe %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 >= 0.6) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

#10% error:
fast_1 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 >= 0.6) %>% 
  filter(error == 0.1) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c)) 

#30% error:
fast_3 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 >= 0.6) %>% 
  filter(error == 0.3) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c)) 

#50% error:
fast_5 <- err_rep5u %>%
  filter(r_s == -0.01767) %>% 
  filter(r_0 >= 0.6) %>% 
  filter(error == 0.5) %>% 
  group_by(id) %>% 
  summarize(cumulative_yield = sum(c))

##Calculate average catch:
avg_perf_fast <- mean(fast_perfect$cumulative_yield)
avg_fishe_fast <- mean(fast_fishe$cumulative_yield)
avg_fast1 <- mean(fast_1$cumulative_yield)
avg_fast3 <- mean(fast_3$cumulative_yield)
avg_fast5 <- mean(fast_5$cumulative_yield)


##Turn those numbers into a dataframe so you can make a table:
error <- c(0.1, 0.3, 0.5)
sims_f <- c(avg_fast1, avg_fast3, avg_fast5)

yield_fast <- data.frame(error = error, perfect = rep(avg_perf_fast, 3), perfect_fishe = rep(avg_fishe_fast, 3),
                         fishe_sims = sims_f) %>% 
  mutate(percent_perfect = (fishe_sims / perfect_fishe) * 100) #Note this is how close the simulations get to perfect given FISHE



##Alternative way to make the table:
yield_fast2 <- data.frame(perfect = avg_perf_fast, perfect_fishe = avg_fishe_fast, error_0.1 = avg_fast1,
                          error_0.3 = avg_fast3, error_0.5 = avg_fast5) 

#Need to calculate the percent of perfect for all the columns:
percent_perf <- 100
percent_perf_fishe_f <- (yield_fast2$perfect_fishe/yield_fast2$perfect) * 100
#note these are calcuting the percent of perfect given FISHE since that's as good as it can possibly be
percent_perf_f0.1 <- (yield_fast2$error_0.1/yield_fast2$perfect_fishe) * 100
percent_perf_f0.3 <- (yield_fast2$error_0.3/yield_fast2$perfect_fishe) * 100
percent_perf_f0.5 <- (yield_fast2$error_0.5/yield_fast2$perfect_fishe) * 100

#Add the row to the dataframe:
yield_int2 <- add_row(yield_fast2, perfect = percent_perf, perfect_fishe = percent_perf_fishe_f, error_0.1 = percent_perf_f0.1,
        error_0.3 = percent_perf_f0.3, error_0.5 = percent_perf_f0.5)

#Add row names:
row.names(yield_fast2) = c("cumulative_yield", "percent_perfect")
```

Make a formal table:  

